# Best practices

R code is often organized in packages that can be installed from centralized repositories such as CRAN or GitHub.
If you are new to writing R packages, this course cannot give a complete introduction into packages.
It is still useful to embrace some very few concepts of R packages to gain access to a vast toolbox and also organize your code in a standardized way familiar to other users.
With the first steps in place, the road to your first R package may become less steep.

- Create a `DESCRIPTION` file to declare dependencies and allow easy reloading of the functions you define
- Store your functions in `.R` files in the `R/` directory in your project
    - Scripts that you execute live in `script/` or a similar directory
- Use [roxygen2](https://github.com/klutometis/roxygen) to document your functions close to the source
- Write tests for your functions, e.g. with [testthat](https://testthat.r-lib.org/)

See [R packages](http://r-pkgs.had.co.nz/) for a more comprehensive treatment.


## DESCRIPTION

Create and open a new RStudio project.
Then, create a `DESCRIPTION` file with `usethis::use_description()`:

```r
# install.packages("usethis")
usethis::use_description()
```

Double-check success:

```r
# install.packages("devtools")
devtools::load_all()
```

Declare that your project requires the tidyverse and the here package:

```r
usethis::use_package("here")
# Currently doesn't work, add manually
# https://github.com/r-lib/usethis/issues/760
# usethis::use_package("tidyverse")
```




## R

With a `DESCRIPTION` file defined, create a new `.R` file and save it in the `R/` directory.
(Create this directory if it does not exist.)
Create a function in this file, save the file:

```{r}
hi <- function(text = "Hello, world!") {
  print(text)
  invisible(text)
}
```

Do not source the file.

Restart R (with Ctrl + Shift + F10 in RStudio).

Run `devtools::load_all()` again, you can use the shortcut Ctrl + Shift + L or Cmd + Shift + L in RStudio.

Check that you can run `hi()` in the console:

```{r}
hi()
hi("Wow!")
```

Edit the function:

```{r}
hi <- function(text = "Wow!") {
  print(text)
  invisible(text)
}
```

Save the file, but do not source it.

Run `devtools::load_all()` again, you can use the shortcut Ctrl + Shift + L or Cmd + Shift + L in RStudio.

Check that the new implementation of `hi()` is active:

```{r}
hi()
```

All functions that are required for your project are stored in this directory.
Do not store executable scripts, use a `script/` directory.


## roxygen2

The following intuitive annotation syntax is a standard way to create documentation for your functions:

```{r}
#' Print a welcome message
#' 
#' This function prints "Wow!", or a custom text, on the console.
#'
#' @param text The text to print, "Wow!" by default.
#' 
#' @return The `text` argument, invisibly.
#' 
#' @examples
#' hi()
#' hi("Hello!")
hi <- function(text = "Wow!") {
  print(text)
  invisible(text)
}
```

This annotation can be rendered to a nicely looking HTML page with the roxygen2 and pkgdown packages.
All you need to do is provide (and maintain) it.



## testthat

Automated tests make sure that the functions you write today continue working tomorrow.
Create your first test with `usethis::use_test()`:

```r
# install.packages("testthat")
usethis::use_test("hi")
```

The file `tests/testthat/test-hi.R` is created, with the following contents:

```r
test_that("multiplication works", {
  expect_equal(2 * 2, 4)
})
```

Replace this predefined text with a test that makes more sense for us:

```r
test_that("hi() works", {
  expect_output(hi(), "Wow")
  expect_output(hi("Hello"), "Hello")
})
```

Run the new test with `devtools::test()`, you can use the shortcut Ctrl + Shift + T or Cmd + Shift + T in RStudio.

Check that the test actually detects failures by modifying the implementation of `hi()` and rerunning the test:

```{r}
hi <- function(text = "Oops!") {
  print(text)
  invisible(text)
}
```

Run the new test with `devtools::test()`, you can use the shortcut Ctrl + Shift + T or Cmd + Shift + T in RStudio.
One test should be failing now.
