---
title: "Programming in the tidyverse"
author: "Kirill Müller, Tobias Schieferdecker"
date: "`r format(lubridate::with_tz(Sys.time(), 'CET'), '%d %B %Y, %H:%M %Z')`"
documentclass: "book"
site: bookdown::bookdown_site
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache = TRUE)
options(tibble.print_min = 3, tibble.print_max = 5, max.print = 20)
if (!knitr::is_latex_output()) {
  options(crayon.enabled = TRUE, pillar.bold = TRUE)
  fansi::set_knit_hooks(knitr::knit_hooks)
}
library(here)

tidyprog_repo <- function(...) {
  file.path("https://github.com/krlmlr/tidyprog-proj/tree/2019-05-zhr", ...)
}
```


# Preface {-}

Material for the [zhRcourse workshop "Programming in the tidyverse"](https://www.zhrcourses.uzh.ch/en/programm2019/tidyverse.html) on May 10, 2019.

## Links {-}

- This website: https://bit.ly/tidyprog
    - Longer URL: https://krlmlr.github.io/tidyprog/

- Scripts and installation instructions: `r tidyprog_repo()`
    - Prepared scripts: `r tidyprog_repo("script")`
    - Live code: `r tidyprog_repo("live")`
    - The code **will be updated live** with a delay of a few seconds during the workshop, it is **not necessary** to repeat the instructor's typing

- rstudio.cloud server: https://rstudio.cloud/project/329883
    - Sign up, or log in with Google or GitHub
    - Click the "Save a private copy" link next to the **TEMPORARY** label in red in the header
    - All necessary packages are preinstalled

## Package versions used {-}

<details><summary>Click to expand</summary>

```{r include = FALSE}
library(tidyverse)
library(here)
```

```{r}
withr::with_options(list(width = 80), print(sessioninfo::session_info()))
```

</details>
