```{r 02-remove-all, include = FALSE}
rm(list = ls())
```


## Vectors and columns

<details><summary>*Click here to make setup code visible*</summary>
```{r include = FALSE}
### Vectors and columns

```
```{r 02-setup-02-dir-r}
library(tidyverse)
library(here)
```
</details>

Here we briefly show the relationship between columns of data frames and their corresponding vectors, i.e. the answer to "how to get from one to the other?":

We can e.g. get a vector with the files in a specific directory of our current project^[function `here::here()` is taking care of making sure we start from the root directory of our current project] like this:

```{r include = FALSE}
# Show all files, see also fs::dir_ls()
```
```{r 02-show-all-files-see-also-fs-dir-ls}
files <- dir(here("data/weather"), full.names = TRUE)
files
```

You can create a tibble from it using `tibble::enframe()`:

```{r include = FALSE}
# Convert to a tibble
```
```{r 02-convert-to-a-tibble}
files_df <-
  files %>%
  enframe()

files_df
```

The `name` column might be unwanted in some cases. Suppress its creation by setting `name = NULL`:

```{r include = FALSE}
# Remove the name column
```
```{r 02-remove-the-name-column}
files_df_1 <-
  files %>%
  enframe(name = NULL)

files_df_1
```

Another way to create a tibble from a vector is using `tibble::tibble()`. 
You can name the newly created columns by assigning the vectors they are created from to (quoted or unquoted) column names:

```{r include = FALSE}
# Construct tibble from a vector
```
```{r 02-construct-tibble-from-a-vector}
tibble(filename = files)
```

The other direction -- producing a vector from a tibble column -- works with `dplyr::pull()`. 
By default `pull()` will turn the rightmost column into a vector and ignore the rest of the tibble:

```{r include = FALSE}
# Extract a column as a vector
```
```{r 02-extract-a-column-as-a-vector}
files_df %>%
  pull()
```

Turn a specific column into a vector by providing the desired column name to `pull()`, either quoted or unquoted:

```{r include = FALSE}
# Extract a specific column as a vector
```
```{r 02-extract-a-specific-column-as-a-vector}
files_df %>%
  pull(name)
```
