```{r 03-remove-all, include = FALSE}
rm(list = ls())
```


## Named vectors and two-column tibbles {#names}

<details><summary>*Click here to make setup code visible*</summary>
```{r include = FALSE}
### Named vectors and two-column tibbles

```
```{r 03-setup-03-names-r}
library(tidyverse)
library(here)
```
</details>

Here we look at tidyverse-functions to work with named vectors and tibbles with more columns and the relations netween the two.

As seen in section ["Data"](#intro-data), load a table -- here a dictionary detailing information related to an id-like name -- from an MS Excel file with `readxl::read_excel()`:

```{r include = FALSE}
# Load dictionary from file
```
```{r 03-load-dictionary-from-file}
dict <- readxl::read_excel(here("data/cities.xlsx"))
dict
```

Use `pull()` as seen in the last chapter:

```{r include = FALSE}
# Acquire file names
```
```{r 03-acquire-file-names}
dict %>%
  pull(weather_filename)
```

Create absolute paths using `here::here()`:

```{r include = FALSE}
# Use here() to create absolute paths
```
```{r 03-use-here-to-create-absolute-paths}
dict %>%
  pull(weather_filename) %>%
  here()
```

Produce a named vector with `tibble::deframe()`, which is thought as the inverse function to `enframe()`.
When given a 2-column tibble, `deframe()` will by default use the first column for the names and the second column for the values of the resulting vector.
When given a 1-column tibble, it creates an unnamed vector.
When given a more-than-2-column tibble, it will use the first two columns as name- and value-columns for the resulting vector, ignore the rest and in addition give a warning that it expects a one- or two-column data frame.

```{r include = FALSE}
# Acquire file names as a named vector
```
```{r 03-acquire-file-names-as-a-named-vector}
weather_filenames <-
  dict %>%
  select(city_code, weather_filename) %>%
  deframe()
weather_filenames
```

The `names()` function accesses the names of a vector:

```{r include = FALSE}
# Use names() to access names
```
```{r 03-use-names-to-access-names}
weather_filenames %>%
  names()
```


Some operations producing vectors from vectors cause the names to be lost:

```{r include = FALSE}
# Not all operations maintain vector names!
```
```{r 03-not-all-operations-maintain-vector-names}
weather_filenames %>%
  here()
```

A possible solution can be in many cases to change the order of the transformations, so that the creation of the named vector comes last (or at least later):

```{r include = FALSE}
# Move the here() call into "tibble-land"
```
```{r 03-move-the-here-call-into-tibble-land}
dict %>%
  mutate(weather_filename_here = here(weather_filename)) %>%
  select(city_code, weather_filename_here) %>%
  deframe()
```

### Exercises

1. Obtain a mapping between city code and city name as a named vector.
    
    ```r
    dict %>% 
      select(___, ___) %>% 
      deframe()
    ```
    
    ```{r echo = FALSE}
    dict %>% 
      select(city_code, name) %>% 
      deframe()
    ```

1. Convert the output of `fs::dir_info()` to that seen from `fs::dir_ls()`. How do you make sure that the vector is named?

    ```r
    # install.packages("fs")
    fs::dir_info()
    fs::dir_info() %>% 
      pull(___)
    fs::dir_info() %>%
      select(_____, _____) %>% 
      ___()
    ```

    ```{r echo = FALSE}
    fs::dir_info()
    fs::dir_info() %>% 
      pull(path)
    fs::dir_info() %>% 
      select(name = path, path) %>% 
      deframe()
    ```
