```{r 04-remove-all, include = FALSE}
rm(list = ls())
```

## Indexing {#indexing}

<details><summary>*Click here to make setup code visible*</summary>
```{r include = FALSE}
### Indexing

```
```{r 04-setup-04-index-r}
library(tidyverse)
library(here)

dict <- readxl::read_excel(here("data/cities.xlsx"))
```
</details>

Here we look at the indexing of a named vector (works equivalently for a named list).

We start with the data frame `dict` from section ["Named vectors and two-column tibbles"](#names).
Create named vector of the -- future -- input files:

```{r include = FALSE}
# Collect input files as a named vector
```
```{r 04-collect-input-files-as-a-named-vector}
input_files <-
  dict %>%
  select(city_code, weather_filename) %>%
  deframe()
input_files
names(input_files)
```

There are different ways of accessing individual entries of the named vector:

```{r include = FALSE}
# Access individual input files
```
```{r 04-access-individual-input-files}
input_files[1]
input_files[[1]]
input_files[["berlin"]]
```

Choose multiple entries with:

```{r include = FALSE}
# Access multiple input files
```
```{r 04-access-multiple-input-files}
input_files[1:2]
input_files[c("berlin", "zurich")]
```
