```{r 06-remove-all, include = FALSE}
rm(list = ls())
```


## Manipulating all datasets {#map_manip}

<details><summary>Setup code</summary>
```{r include = FALSE}
### Manipulating all datasets

```
```{r 06-setup-05-map-manip-r}
library(tidyverse)
library(here)

dict <- readxl::read_excel(here("data/cities.xlsx"))

input_data <-
  dict %>%
  select(city_code, weather_filename) %>%
  deframe() %>%
  map(~ readxl::read_excel(here(.)))
```
</details>

How to selectively manipulate specific parts of a list of datasets?

We start with the named list of tibbles called `input_data` from section ["Processing all files"](#map).
Of each tibble we only want the column `time` and all the columns whose name contains "emperature":

```{r include = FALSE}
# Manipulate results
```
```{r 06-manipulate-results}
input_data %>%
  map(~ select(., time, contains("emperature")))
```

But we don't want all of the observations, respectively. 
We only want those with values in column `temperature` greater or equal than 14°C:

```{r include = FALSE}
# Manipulate results more
```
```{r 06-manipulate-results-more}
input_data %>%
  map(~ select(., time, contains("emperature"))) %>%
  map(~ filter(., temperature >= 14))
```

Create a custom function for that specific purpose in a call to `map()`:

```{r include = FALSE}
# Create a function to manipulate
```
```{r 06-create-a-function-to-manipulate}
manipulator <- function(data) {
  data %>%
    select(time, contains("emperature")) %>%
    filter(temperature >= 14)
}
```

Let's look at the object `manipulator`, that we created:

```{r include = FALSE}
# Functions are first-class objects!
```
```{r 06-functions-are-first-class-objects}
manipulator
```

Testing the function:

```{r include = FALSE}
# Test the function
```
```{r 06-test-the-function}
manipulator(input_data[[4]])
```

Now let's use `map()` to let our function act on the entire dataset:

```{r include = FALSE}
# Run the function on the entire dataset
```
```{r 06-run-the-function-on-the-entire-dataset}
manipulated_data <- map(input_data, ~ manipulator(.))
manipulated_data
```

`map()` also allows for other notations, e.g.:

```{r include = FALSE}
# Shortcut
```
```{r 06-shortcut}
map(input_data, manipulator)
```
