```{r 01-remove-all, include = FALSE}
rm(list = ls())
```


## Review of visualization and data transformation

This section is a refresher for visualization and data transformation in the tidyverse.
Readers familiar with the first half or [R for data science](https://r4ds.had.co.nz/) will recognize the concepts repeated here.
The data used throughout this course is presented, plotted and briefly analyzed.

The code in each chapter is self-contained.
The code in each section is also self-contained, but the necessary setup code is hidden and can be expanded with a click.
We will always load the following packages:

```{r include = FALSE}
### Review of visualization and data transformation

```
```{r 01-setup-01-intro-r}
library(tidyverse)
library(here)
```

Functions from other packages may be used with the `::` notation.


### Data {#intro-data}

We will be working with hourly measurements of weather data ([link to data documentation](https://darksky.net/dev/docs)) in four cities (Berlin, Toronto, Tel Aviv and Zurich) between 2019-04-28, 3pm and 2019-04-30, 3pm.
Thus we have 49 observations in each city.
Variables are:

- `time`
- `summary` (how to describe the weather in one word)
- `icon` (mix of description of weather plus time of day)
- `precipIntensity` (intensity of precipitation [mm/h])
- `precipProbability`
- `temperature`
- `apparentTemperature`
- `dewPoint`
- `humidity`
- `pressure`
- `windSpeed`
- `windGust`
- `windBearing` (direction in degrees)
- `cloudCover`
- `uvIndex`
- `visibility`
- `ozone`
- `precipType`


Reading in the data, which is stored in MS Excel-Files:

```{r include = FALSE}
# Read all files
```
```{r 01-read-all-files}
berlin <- readxl::read_excel(here("data/weather", "berlin.xlsx"))
toronto <- readxl::read_excel(here("data/weather", "toronto.xlsx"))
tel_aviv <- readxl::read_excel(here("data/weather", "tel_aviv.xlsx"))
zurich <- readxl::read_excel(here("data/weather", "zurich.xlsx"))
```

Create one larger tibble from the four smaller ones:

```{r include = FALSE}
# Create ensemble dataset
```
```{r 01-create-ensemble-dataset}
weather_data <- bind_rows(
  berlin = berlin,
  toronto = toronto,
  tel_aviv = tel_aviv,
  zurich = zurich,
  .id = "city_code"
)
```

### Exploration

```{r include = FALSE}
# Show the data
```
```{r 01-show-the-data}
weather_data
```

Example plot of humidity vs. pressure (`geom_path()` ensures that points are connected according to their order in the tibble):

```{r include = FALSE}
# Visibility vs. humitidy
```
```{r 01-visibility-vs-humitidy}
weather_data %>%
  ggplot(aes(x = pressure, y = humidity, color = city_code)) +
  geom_path()
```

Barplots of number of occurences of each kind of weather per city:

```{r include = FALSE}
# Summary
```
```{r 01-summary}
weather_data %>%
  ggplot(aes(x = city_code)) +
  geom_bar(aes(fill = summary))

weather_data %>%
  ggplot(aes(x = city_code)) +
  geom_bar(aes(fill = summary), position = position_dodge2("dodge", preserve = "single"))
```

Lineplot with different line types and an additional visualisation of the line range (here, difference between apparent and actual temperature):

```{r include = FALSE}
# Temperature and apparent temperature
```
```{r 01-temperature-and-apparent-temperature}
temperature_data <-
  weather_data %>%
  select(city_code, time, temperature, apparentTemperature) %>%
  gather(kind, temperature, -city_code, -time) %>%
  mutate(apparent = (kind == "apparentTemperature")) %>%
  select(-kind)

temperature_data %>%
  ggplot(aes(x = time, color = city_code)) +
  geom_linerange(data = weather_data, aes(ymin = temperature, ymax = apparentTemperature)) +
  geom_line(aes(linetype = apparent, y = temperature))
```

Relation of temperature difference between actual and apparent temperature (cf. line range in last plot) with wind speed, shown as scatter plot.

```{r include = FALSE}
# Compute and plot temperature difference
```
```{r 01-compute-and-plot-temperature-difference}
weather_data %>%
  mutate(apparentTemperatureReduction = temperature - apparentTemperature) %>%
  filter(city_code != "tel_aviv") %>%
  ggplot(aes(x = windSpeed, y = apparentTemperatureReduction)) +
  geom_point(aes(color = city_code))
```

### Further dplyr transformations

If you want to compare measurements of the same observable at two different points in time, maybe the most straightforward way to do so is to create a new column with an appropriate lag:

```{r include = FALSE}
# Compute lag for temperature, pressure and humidity.
# How to compute temperature difference to previous hour?
```
```{r 01-compute-lag-for-temperature-pressure-and-humidity}
weather_data %>%
  group_by(city_code) %>%
  mutate_at(vars(temperature, pressure, humidity), list(lag = lag)) %>%
  ungroup()
```


Count observations per category or combinations of categories:

```{r include = FALSE}
# Count observations
```
```{r 01-count-observations}
weather_data %>%
  count(city_code)

weather_data %>%
  count(city_code, summary)
```

Use `summarize()` to create a tibble with mean and maximum temperature for each city:

```{r include = FALSE}
# Compute mean and max temperature
```
```{r 01-compute-mean-and-max-temperature}
weather_data %>%
  group_by(city_code) %>%
  summarize(temperature_mean = mean(temperature), temperature_max = max(temperature)) %>%
  ungroup()
```

Compute and display summary data for all numeric variables:

```{r include = FALSE}
# Compute and display summary data for all numeric variables
```
```{r 01-compute-and-display-summary-data-for-all-numeric-variables}
weather_data %>%
  group_by(city_code) %>%
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, max = max)) %>%
  ungroup() %>%
  gather(key, value, -city_code) %>%
  separate(key, into = c("indicator", "fun")) %>%
  xtabs(value ~ city_code + indicator + fun, .) %>%
  ftable()
```
