```{r 12-remove-all, include = FALSE}
rm(list = ls())
```


## Moving to tibble-land {#mut_map}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Moving to tibble-land

```
```{r 12-setup-12-mutate-map-r}
library(tidyverse)
library(here)

dict <- readxl::read_excel(here("data/cities.xlsx"))

input_data <-
  dict %>%
  select(city_code, weather_filename) %>%
  deframe() %>%
  map(~ readxl::read_excel(here(.)))
```
</details>

How to combine the abilities of `map()` & co., which work on vectors and lists, with our commonly used data structure, the tibble?

We start with the named list of tibbles called `input_data` from section ["Processing all files"](#map) and with `dict` from section ["Named vectors and two-column tibbles"](#names).

Produce a data frame from `input_data` with `enframe()` leads to a maybe at first surprising, but oftentimes useful result:

```{r include = FALSE}
# Lists are also vectors, enframe() returns a nested tibble!
```
```{r 12-lists-are-also-vectors-enframe-returns-a-nested-tibble}
input_data %>%
  enframe()
```

This is because lists are also vectors.
In our case each list entry contains a tibble, which can be "nested" into each entry of column `value`.

Starting with the tibble `dict` we can see how `dpylr::mutate()` and `map()` can nicely work together to produce a somewhat similar result:

```{r include = FALSE}
# Operate in "tibble-land" right away: columns are vectors
```
```{r 12-operate-in-tibble-land-right-away-columns-are-vectors}
dict %>%
  select(city_code, weather_filename) %>%
  mutate(
    data = map(weather_filename, ~ readxl::read_excel(here(.)))
  )
```

This works because `R` interprets columns of tibbles as vectors, which can be fed to `map()`.

Deselect i.e. drop columns using `select()` with `-`:

```{r include = FALSE}
# Keep important columns
```
```{r 12-keep-important-columns}
dict_data <-
  dict %>%
  mutate(
    data = map(weather_filename, ~ readxl::read_excel(here(.)))
  ) %>%
  select(-weather_filename)
dict_data
```
