```{r 21-remove-all, include = FALSE}
rm(list = ls())
```


## Definition and execution

The following packages are used for this chapter.

```{r include = FALSE}
### Definition and execution

```
```{r 21-setup-31-function-r}
library(tidyverse)
library(here)
```


```{r include = FALSE}
# Important! Please reset the R session before running this script.
# (In RStudio: Session/Restart R)
```
```{r 21-important-please-reset-the-r-session-before-running-this-script}

```

Create functions for tasks that need to be executed repeatedly, or to hide implementation details.

```{r include = FALSE}
# Declare a function to hide implementation details
```
```{r 21-declare-a-function-to-hide-implementation-details}
read_weather_data <- function() {
  # Read all files
  berlin <- readxl::read_excel(here("data/weather", "berlin.xlsx"))
  toronto <- readxl::read_excel(here("data/weather", "toronto.xlsx"))
  tel_aviv <- readxl::read_excel(here("data/weather", "tel_aviv.xlsx"))
  zurich <- readxl::read_excel(here("data/weather", "zurich.xlsx"))

  # Create ensemble dataset
  weather_data <- bind_rows(
    berlin = berlin,
    toronto = toronto,
    tel_aviv = tel_aviv,
    zurich = zurich,
    .id = "city_code"
  )

  # Return it
  weather_data
}
```

Display the code of any function by writing its name without the subsequent parentheses:

```{r include = FALSE}
# Functions are first-class objects
```
```{r 21-functions-are-first-class-objects}
read_weather_data
```

Call the function by adding the parentheses:

```{r include = FALSE}
# Call like functions exported from packages
```
```{r 21-execute-like-functions-exported-from-packages}
read_weather_data()
```


Execution of the function does not create new variables in the global environment.
The only object in the global environment is the function itself:

```{r include = FALSE}
# Variables are local, execution doesn't change global variables.
# (The effect is only seen when starting R in a fresh session.)
```
```{r 21-variables-are-local-execution-doesn-t-change-global-variables}
ls()
```

A function can also be used as input for a pipe:

```{r include = FALSE}
# Pipe
```
```{r 21-pipe}
read_weather_data() %>% 
  count(city_code)
```

To reuse a function value, assign it to a variable:

```{r include = FALSE}
# Assign result to use in further operations
```
```{r 21-assign-result-to-use-in-further-operations}
weather_data <- read_weather_data()
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. Create a modified version of the function to return only data for Toronto and Tel Aviv. Call it.

    ```r
    read_weather_data_non_europe <- function() {
      _______
    }
    
    _______
    ```
    
    ```{r echo = FALSE}
    read_weather_data_non_europe <- function() {
      # Read non-Europe files
      toronto <- readxl::read_excel(here("data/weather", "toronto.xlsx"))
      tel_aviv <- readxl::read_excel(here("data/weather", "tel_aviv.xlsx"))
    
      # Create ensemble dataset
      weather_data <- bind_rows(
        toronto = toronto,
        tel_aviv = tel_aviv,
        .id = "city_code"
      )
    
      # Return it
      weather_data
    }
    
    read_weather_data_non_europe()
    ```
    

1. Compute number of rows for Europe, count observations to validate:

    ```r
    nrow(_____) - nrow(_____)
    ```
    
    ```{r echo = FALSE}
    # Double-check:
    nrow(read_weather_data()) - nrow(read_weather_data_non_europe())
    ```
