```{r 22-remove-all, include = FALSE}
rm(list = ls())
```


## Arguments {#args}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Arguments

```
```{r 22-setup-22-args-r}
library(tidyverse)
library(here)
```
</details>

By adding arguments to your functions, you can turn them into tools for a wide range of applications.
But it is advisable to be conservative here: try to minimise the number of arguments to the necessary ones, so the user has a clear and intuitive interface to deal with.

Functions with arguments:

```{r include = FALSE}
# Functions can have arguments
```
```{r 22-functions-can-have-arguments}
weather_path <- function(filename) {
  # Returned value
  here("data/weather", filename)
}

weather_path("milan.xlsx")
```

Call functions from within functions:

```{r include = FALSE}
# Functions can be called by other functions
```
```{r 22-functions-can-be-called-by-other-functions}
read_weather_data <- function() {
  # Read all files
  berlin <- readxl::read_excel(weather_path("berlin.xlsx"))
  toronto <- readxl::read_excel(weather_path("toronto.xlsx"))
  tel_aviv <- readxl::read_excel(weather_path("tel_aviv.xlsx"))
  zurich <- readxl::read_excel(weather_path("zurich.xlsx"))

  # Create ensemble dataset
  weather_data <- bind_rows(
    berlin = berlin,
    toronto = toronto,
    tel_aviv = tel_aviv,
    zurich = zurich,
    .id = "city_code"
  )

  # Return it
  weather_data
}
```

The function still needs to be called for testing it.
It is a good practice to always immediately test a the newly created or updated function by running it:

```{r include = FALSE}
# Still need to run a function
```
```{r 22-still-need-to-run-a-function}
read_weather_data()
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. How does the behavior of `read_weather_data()` change if we update the definition of the `read_weather()` function as follows:

    ```r
    weather_path <- function(filename) {
      # Returned value
      here("data", "weather", filename)
    }
    ```
    
    Hint: Define this function with a different name and check its output values, before running `read_weather_data()` again.
