```{r 23-remove-all, include = FALSE}
rm(list = ls())
```


## Use case: Intermediate variables {#intermediate}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Use case: Intermediate variables

```
```{r 23-setup-33-intermediate-r}
library(tidyverse)
library(here)

weather_path <- function(filename) {
  # Returned value
  here("data/weather", filename)
}
```
</details>

We start with the function `weather_path()` from section ["Arguments"](#args).

Functions can help to avoid having to use intermediate variables:

```{r include = FALSE}
# Functions can help eliminate intermediate variables
```
```{r 23-functions-can-help-eliminate-intermediate-variables}
read_weather_file <- function(filename) {
  readxl::read_excel(weather_path(filename))
}

read_weather_data <- function() {
  # Create ensemble dataset from files on disk
  weather_data <- bind_rows(
    berlin = read_weather_file("berlin.xlsx"),
    toronto = read_weather_file("toronto.xlsx"),
    tel_aviv = read_weather_file("tel_aviv.xlsx"),
    zurich = read_weather_file("zurich.xlsx"),
    .id = "city_code"
  )

  # Return it
  weather_data
}

read_weather_data()
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. Implement a helper function `get_weather_file_for()` that takes a city code as input and returns the file name for the corresponding Excel file. Intended usage: `get_weather_file_for("berlin")`. Test this function on a few example inputs.

    ```r
    get_weather_file_for <- _____ {
      paste0(city_code, ".xlsx")
    }
    ```
    
    ```{r echo = FALSE}
    # Operate on city codes, not file names:
    get_weather_file_for <- function(city_code) {
      paste0(city_code, ".xlsx")
    }
    ```
        
    ```{r}
    get_weather_file_for("munich")
    get_weather_file_for("san_diego")
    ```


1. Implement a helper function `get_weather_data_for()` that takes a city code as input (as opposed to a file name). Intended usage: `get_weather_data_for("berlin")`. Update `read_weather_data()` to use `get_weather_data_for()`.

    ```r
    get_weather_data_for <- _____ {
      read_weather_file(_____)
    }
    ```
    
    ```{r echo = FALSE}
    # High-level reader:
    get_weather_data_for <- function(city_code) {
      read_weather_file(get_weather_file_for(city_code))
    }
    ```
    
    ```{r}
    get_weather_data_for("toronto")
    ```
