```{r 24-remove-all, include = FALSE}
rm(list = ls())
```


## Default values

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Default values

```
```{r 24-setup-24-args-default-r}
library(tidyverse)
library(here)


weather_path <- function(filename) {
  # Returned value
  here("data/weather", filename)
}

read_weather_file <- function(filename) {
  readxl::read_excel(weather_path(filename))
}

get_weather_file_for <- function(city_code) {
  paste0(city_code, ".xlsx")
}

get_weather_data_for <- function(city_code) {
  read_weather_file(get_weather_file_for(city_code))
}
```
</details>

For user-friendliness it is often good practice to provide default values for parameters

We start with the function`get_weather_data_for()` from section ["Intermediate variables"](#intermediate).

Here an example of a boolean argument which when `TRUE` leads to dropping the data about Zurich.

```{r include = FALSE}
# Function arguments can have default values
```
```{r 24-function-arguments-can-have-default-values}
read_weather_data <- function(omit_zurich = FALSE) {
  # Create ensemble dataset from files on disk
  weather_data <- bind_rows(
    berlin = get_weather_data_for("berlin"),
    toronto = get_weather_data_for("toronto"),
    tel_aviv = get_weather_data_for("tel_aviv"),
    zurich = get_weather_data_for("zurich"),
    .id = "city_code"
  )

  # Return it (filtered)
  weather_data %>%
    filter( !(city_code == "zurich" & omit_zurich) )
}
```


Set arguments with default values explicitly with or without using the name or leave them out to use the default value:

```{r include = FALSE}
# Function arguments can be called by name or by position,
# optional arguments are omitted
```
```{r 24-function-arguments-can-be-called-by-name-or-by-position}
read_weather_data(TRUE)
read_weather_data(omit_zurich = TRUE)
read_weather_data()
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. Update `get_weather_data_for()` to return Zurich data if called without arguments. Is this a good idea?

    ```r
    get_weather_data_for <- _____ {
      _____
    }
    ```
    
    ```{r echo = FALSE}
    # Default city:
    get_weather_data_for <- function(city_code = "zurich") {
      read_weather_file(get_weather_file_for(city_code))
    }
    
    # Test:
    ```
    
    ```{r}
    get_weather_data_for() %>% 
      select(temperature)
    get_weather_data_for("tel_aviv") %>% 
      select(temperature)
    ```
