```{r 24-remove-all, include = FALSE}
rm(list = ls())
```


## Default values

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Default values

```
```{r 24-setup-34-args-default-r}
library(tidyverse)
library(here)


weather_path <- function(filename) {
  # Returned value
  here("data/weather", filename)
}
read_weather_file <- function(filename) {
  readxl::read_excel(weather_path(filename))
}
```
</details>

For user-friendliness it is often good practice to provide default values for parameters

We start with the functions `weather_path()` from section ["Arguments"](#args) and `read_weather_file()` from section ["Intermediate variables"](#intermediate).

Here an example of a boolean argument which when `TRUE` leads to dropping the data about Zurich.

```{r include = FALSE}
# Function arguments can have default values
```
```{r 24-function-arguments-can-have-default-values}
read_weather_data <- function(omit_zurich = FALSE) {
  # Create ensemble dataset from files on disk
  weather_data <- bind_rows(
    berlin = read_weather_file("berlin.xlsx"),
    toronto = read_weather_file("toronto.xlsx"),
    tel_aviv = read_weather_file("tel_aviv.xlsx"),
    zurich = read_weather_file("zurich.xlsx"),
    .id = "city_code"
  )

  # Return it (filtered)
  weather_data %>%
    filter( !(city_code == "zurich" & omit_zurich) )
}
```


Set arguments with default values explicitly with or without using the name or leave them out to use the default value:

```{r include = FALSE}
# Function arguments can be called by name or by position,
# optional arguments are omitted
```
```{r 24-function-arguments-can-be-called-by-name-or-by-position}
read_weather_data(TRUE)
read_weather_data(omit_zurich = TRUE)
read_weather_data()
```
