```{r 25-remove-all, include = FALSE}
rm(list = ls())
```


## Multiple arguments

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Multiple arguments

```
```{r 25-setup-35-args-multi-r}
library(tidyverse)
library(here)


weather_path <- function(filename) {
  # Returned value
  here("data/weather", filename)
}

read_weather_file <- function(filename) {
  readxl::read_excel(weather_path(filename))
}

get_weather_file_for <- function(city_code) {
  paste0(city_code, ".xlsx")
}

get_weather_data_for <- function(city_code) {
  read_weather_file(get_weather_file_for(city_code))
}
```
</details>

We start once more with the functions `weather_path()` from section ["Arguments"](#args) and `get_weather_data_for()` from section ["Intermediate variables"](#intermediate).

What are the considerations when using multiple function arguments?
You can add new parameters in a very straightforward manner like this:

```{r include = FALSE}
# Multiple function arguments are separated by comma:
```
```{r 25-multiple-function-arguments-are-separated-by-comma}
read_weather_data <- function(omit_zurich = FALSE, omit_toronto = FALSE) {
  # Create ensemble dataset from files on disk
  weather_data <- bind_rows(
    berlin = get_weather_data_for("berlin"),
    toronto = get_weather_data_for("toronto"),
    tel_aviv = get_weather_data_for("tel_aviv"),
    zurich = get_weather_data_for("zurich"),
    .id = "city_code"
  )

  # Return it (filtered)
  weather_data %>%
    filter( !(city_code == "zurich" & omit_zurich) ) %>%
    filter( !(city_code == "toronto" & omit_toronto) )
}
```

Use the so called ellipsis (`...`) when you want to provide the possibility for the user to call your function with a list of arguments of unspecified length. 
This can be e.g. useful for passing arguments downstream:

```{r include = FALSE}
# Ellipsis: variable argument list, useful for passing arguments downstream
```
```{r 25-ellipsis-variable-argument-list-useful-for-passing-arguments-downstream}
weather_path <- function(...) {
  # All arguments are passed on
  here("data/weather", ...)
}

weather_path("berlin.xlsx")

weather_path("some", "subdir", "with", "a", "file.csv")
```


Mind, that despite altering the original function and adding new features to it, the original call still works as before:

```{r include = FALSE}
# Note: despite many changes and new features,
# the original call still works!
# (This can be tested automatically!)
```
```{r 25-note-despite-many-changes-and-new-features}
read_weather_data()
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. What does the following return? Why?

    ```r
    read_weather_data(TRUE, omit_z = FALSE) %>%
      count(city_code)
    ```

    ```{r include = FALSE}
    # What does the following return? Why?
    read_weather_data(TRUE, omit_z = FALSE) %>%
      count(city_code)
    ```
    
    See the next section for ideas on avoiding this behavior.
