```{r 26-remove-all, include = FALSE}
rm(list = ls())
```


## Argument matching

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Argument matching

```
```{r 26-setup-26-args-matching-r}

```
</details>

How does `R` handle function calls with arguments?

Named arguments are assigned first, after that remaining slots are filled from left to right.

```{r include = FALSE}
# Call matching
```
```{r 26-call-matching}
use_names <- function(one = 1, two = 2) {
  list(one = one, two = two)
}

use_names(3, 4)
use_names(one = 3, 4)
use_names(3, one = 4)
use_names(one = 3, two = 4)
use_names(two = 3, one = 4)
```

Arguments are matched partially, which can be convenient but is also a source of errors.

```{r include = FALSE}
# Partial matching
```
```{r 26-partial-matching}
use_names(o = 3, 4)
use_names(3, o = 4)
use_names(o = 3, t = 4)
use_names(t = 3, o = 4)
```

The ellipsis can be used to enforce the user to fully name the function parameters when setting them:

```{r include = FALSE}
# The ellipsis is useful to enforce naming of arguments
```
```{r 26-the-ellipsis-is-useful-to-enforce-naming-of-arguments}
only_names <- function(..., one = 1, two = 2) {
  list(one = one, two = two)
}

only_names(3, 4)
only_names(one = 3, 4)
only_names(one = 3, two = 4)
only_names(o = 3, t = 4)
```

Inside a function with an ellipsis as a parameter, you can capture the ellipsis with `list()`:

```{r include = FALSE}
# Arguments in ellipsis can be captured via list()
```
```{r 26-arguments-in-ellipsis-can-be-captured-via-list}
ellipsis_test <- function(...) {
  args <- list(...)
  names(args)
}

ellipsis_test(a = 1, 2, c = 3:5)
```

Arguments in ellipsis can be accessed with `..1`, `..2` etc.

```{r include = FALSE}
# Arguments in ellipsis can be accessed with ..1, ..2 etc.
```
```{r 26-arguments-in-ellipsis-can-be-accessed-with-1-2-etc}
ellipsis_direct_test <- function(...) {
  list(..1, ..2)
}

ellipsis_direct_test(a = 1, 2, c = 3:5)
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. Naming, not naming or partly naming parameters in functions calls? What does the following return and why?

    ```{r include = FALSE}
    # Naming, not naming or partly naming parameters in functions calls? What does the following return and why?
    ```
    ```{r echo = TRUE, results = "hide"}
    use_some_names <- function(one = 1, ..., two = 2) {
      list(one = one, two = two)
    }
    
    use_some_names(3, 4)
    use_some_names(one = 3, 4)
    use_some_names(3, one = 4)
    use_some_names(one = 3, two = 4)
    use_some_names(two = 4, 3)
    ```

1. Model a new `enforce_names()` function after `only_names()` to check if any unnamed or misnamed arguments have been used. Test this function in various combinations.

    ```r
    enforce_names <- function(..., one = 1, two = 2) {
      extra_args <- _____
      stopifnot(length(_____) == 0)
    
      list(_____)
    }
    ```

    ```{r include = FALSE}
    ## Program defensively!
    ```
    ```{r 26-program-defensively, echo = FALSE}
    enforce_names <- function(..., one = 1, two = 2) {
      extra_args <- list(...)
      stopifnot(length(extra_args) == 0)
    
      list(one = one, two = two)
    }
    ```
    
    ```{r 26-program-defensively-res}
    try(enforce_names(3, 4))
    try(enforce_names(one = 3, 4))
    try(enforce_names(3, one = 4))
    try(enforce_names(two = 4, 3))
    try(enforce_names(o = 3, t = 4))
    enforce_names(one = 3, two = 4)
    ```
