```{r 31-remove-all, include = FALSE}
rm(list = ls())
```

The following packages are required throughout this chapter:

```{r include = FALSE}
### Vectors and columns

```
```{r 31-setup-02-dir-r}
library(tidyverse)
library(here)
```

## Vectors and columns

So far we focus on the data frame, or tibble, as primary object for data analysis.
Internally, a tibble is a list of vectors of the same length.
Accessing a row in a tibble requires finding the same index in that list of vectors.

Here we explore the relationship between columns of data frames and their corresponding vectors, i.e. the answer to "how to get from one to the other?":

We can e.g. get a vector with the files in a specific directory of our current project^[function `here::here()` is taking care of making sure we start from the root directory of our current project] like this:

```{r include = FALSE}
# Show all files, see also fs::dir_ls()
```
```{r 31-show-all-files-see-also-fs-dir-ls}
files <- dir(here("data/weather"), full.names = TRUE)
files
```

You can create a tibble from it using `tibble::enframe()`:

```{r include = FALSE}
# Convert to a tibble
```
```{r 31-convert-to-a-tibble}
files_df <-
  files %>%
  enframe()

files_df
```

The `name` column might be unwanted in some cases. Suppress its creation by setting `name = NULL`:

```{r include = FALSE}
# Remove the name column
```
```{r 31-remove-the-name-column}
files_df_1 <-
  files %>%
  enframe(name = NULL)

files_df_1
```

Another way to create a tibble from a vector is using `tibble::tibble()`. 
You can name the newly created columns by assigning the vectors they are created from to (quoted or unquoted) column names:

```{r include = FALSE}
# Construct tibble from a vector
```
```{r 31-construct-tibble-from-a-vector}
tibble(filename = files)
```

The other direction -- producing a vector from a tibble column -- works with `dplyr::pull()`. 
By default `pull()` will turn the rightmost column into a vector and ignore the rest of the tibble:

```{r include = FALSE}
# Extract a column as a vector
```
```{r 31-extract-a-column-as-a-vector}
files_df %>%
  pull()
```

Turn a specific column into a vector by providing the desired column name to `pull()`, either quoted or unquoted:

```{r include = FALSE}
# Extract a specific column as a vector
```
```{r 31-extract-a-specific-column-as-a-vector}
files_df %>%
  pull(name)
```

```{r include = FALSE}
# Exercises
```

### Exercises

1. Investigate the output of `fs::dir_ls()` with `enframe()`. Explain.

    ```r
    # install.packages("fs")
    fs::dir_ls()
    fs::dir_ls() %>%
      ___()
    ```
    
    ```{r echo = FALSE}
    fs::dir_ls() %>% 
      enframe()
    ```
