```{r 31-remove-all, include = FALSE}
rm(list = ls())
```


## Basics

```{r include = FALSE}
### Basics

```
```{r 31-setup-31-function-r}
library(tidyverse)
library(here)
```


```{r include = FALSE}
## TODO: Split script, don't overwrite!
```
```{r 31-todo-split-script-don-t-overwrite}

```


```{r include = FALSE}
# Important! Please reset the R session before running this script.
# (In RStudio: Session/Restart R)
```
```{r 31-important-please-reset-the-r-session-before-running-this-script}

```

### Designing functions

Create functions for tasks that need to be executed frequently.

```{r include = FALSE}
# Declare a function to hide implementation details
```
```{r 31-declare-a-function-to-hide-implementation-details}
read_weather_data <- function() {
  # Read all files
  berlin <- readxl::read_excel(here("data/weather", "berlin.xlsx"))
  toronto <- readxl::read_excel(here("data/weather", "toronto.xlsx"))
  tel_aviv <- readxl::read_excel(here("data/weather", "tel_aviv.xlsx"))
  zurich <- readxl::read_excel(here("data/weather", "zurich.xlsx"))

  # Create ensemble dataset
  weather_data <- bind_rows(
    berlin = berlin,
    toronto = toronto,
    tel_aviv = tel_aviv,
    zurich = zurich,
    .id = "city_code"
  )

  # Return it
  weather_data
}
```

Display the code of any function by writing its name without the subsequent brackets:

```{r include = FALSE}
# Functions are first-class objects
```
```{r 31-functions-are-first-class-objects}
read_weather_data
```

Execute the function by adding the brackets:

```{r include = FALSE}
# Execute like functions exported from packages
```
```{r 31-execute-like-functions-exported-from-packages}
read_weather_data()
```


List `R`-objects in an environment:

```{r include = FALSE}
# Variables are local, execution doesn't change global variables.
# (The effect is only seen when starting R in a fresh session.)
```
```{r 31-variables-are-local-execution-doesn-t-change-global-variables}
ls()
```

Assign function values to a variable:

```{r include = FALSE}
# Assign result to use in further operations
```
```{r 31-assign-result-to-use-in-further-operations}
weather_data <- read_weather_data()
```

Functions with arguments:

```{r include = FALSE}
# Functions can have arguments
```
```{r 31-functions-can-have-arguments}
weather_path <- function(filename) {
  # Returned value
  here("data/weather", filename)
}
```

Call functions from within functions:

```{r include = FALSE}
# Functions can be called by other functions
```
```{r 31-functions-can-be-called-by-other-functions}
read_weather_data <- function() {
  # Read all files
  berlin <- readxl::read_excel(weather_path("berlin.xlsx"))
  toronto <- readxl::read_excel(weather_path("toronto.xlsx"))
  tel_aviv <- readxl::read_excel(weather_path("tel_aviv.xlsx"))
  zurich <- readxl::read_excel(weather_path("zurich.xlsx"))

  # Create ensemble dataset
  weather_data <- bind_rows(
    berlin = berlin,
    toronto = toronto,
    tel_aviv = tel_aviv,
    zurich = zurich,
    .id = "city_code"
  )

  # Return it
  weather_data
}
```


```{r include = FALSE}
# Still need to run a function
```
```{r 31-still-need-to-run-a-function}
read_weather_data()
```

Functions can help to avoid using intermediate variables:

```{r include = FALSE}
# Functions can help eliminate intermediate variables
```
```{r 31-functions-can-help-eliminate-intermediate-variables}
read_weather_file <- function(filename) {
  readxl::read_excel(weather_path(filename))
}

read_weather_data <- function() {
  # Create ensemble dataset from files on disk
  weather_data <- bind_rows(
    berlin = read_weather_file("berlin.xlsx"),
    toronto = read_weather_file("toronto.xlsx"),
    tel_aviv = read_weather_file("tel_aviv.xlsx"),
    zurich = read_weather_file("zurich.xlsx"),
    .id = "city_code"
  )

  # Return it
  weather_data
}

read_weather_data()
```


```{r include = FALSE}
### Exercise
```
```{r 31-exercise}

```


```{r include = FALSE}
# Simplify more?
```
```{r 31-simplify-more}

```


```{r include = FALSE}
# Get rid of repeated .xlsx?
```
```{r 31-get-rid-of-repeated-xlsx}

get_weather_for <- function(city) {
  filename <- paste0(city, ".xlsx")

  readxl::read_excel(
    paste0(
      weather_path(filename)
    )
  )
}

weather_path_for <- function(city) {

  here("data/weather", paste0(city, ".xlsx"))
}

get_weather_for2 <- function(city) {
  readxl::read_excel(weather_path_for(city))
}

read_weather_data <- function() {
  # Create ensemble dataset from files on disk
  weather_data <- bind_rows(
    berlin = get_weather_for2("berlin"),
    toronto = get_weather_for2("toronto"),
    tel_aviv = get_weather_for2("tel_aviv"),
    zurich = get_weather_for2("zurich"),
    .id = "city_code"
  )

  # Return it
  weather_data
}

read_weather_data()
```
