```{r 33-remove-all, include = FALSE}
rm(list = ls())
```


## Scope

When working with functions, it is important to be aware of the scope of objects, i.e. what is known in which context?

<!-- Setup 33-function-scoping.R -->
```{r 33-setup-33-function-scoping-r}
a <- 5
```

`a` is now an object of the global environemnt. A function can access global variables:

<!-- A function can access global variables: -->
```{r 33-a-function-can-access-global-variables}
f <- function() {
  a
}

f()
```

On the other hand, a variable which is defined inside a function, will not be known outside of that function. Respectively, it won't overwrite the value of global variables.

<!-- When a function writes to a variable, it always writes in scope -->
```{r 33-when-a-function-writes-to-a-variable-it-always-writes-in-scope}
f <- function() {
  a <- 2
  a
}

f()
a
```


Global variables are a (hidden) part of a function's interface.

<!-- Global variables are a (hidden) part of a function's interface! -->
```{r 33-global-variables-are-a-hidden-part-of-a-function-s-interface}

```

Best practice: functions should be self-contained, independent of global variables.

<!-- Best practice: self-contained functions, independent of global variables -->
```{r 33-best-practice-self-contained-functions-independent-of-global-variables}

```


<!-- ## Exercises: -->
```{r 33-exercises}

```
