```{r 33-remove-all, include = FALSE}
rm(list = ls())
```


## Indexing/subsetting {#indexing}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Indexing/subsetting

```
```{r 33-setup-33-index-r}
library(tidyverse)
library(here)

dict <- readxl::read_excel(here("data/cities.xlsx"))
```
</details>

Here we look at the indexing of a named vector (works equivalently for a named list).

We start with the data frame `dict` from section ["Named vectors and two-column tibbles"](#names).
Create named vector of the -- future -- input files:

```{r include = FALSE}
# Collect input files as a named vector
```
```{r 33-collect-input-files-as-a-named-vector}
input_files <-
  dict %>%
  select(city_code, weather_filename) %>%
  deframe()
input_files
names(input_files)
```

There are different ways of accessing individual entries of the named vector:

```{r include = FALSE}
# Access individual input files
```
```{r 33-access-individual-input-files}
input_files[1]
input_files[[1]]

input_files["berlin"]
input_files[["berlin"]]
```

Choose multiple entries with:

```{r include = FALSE}
# Access multiple input files
```
```{r 33-access-multiple-input-files}
input_files[1:2]
input_files[c("berlin", "zurich")]
```

Consistent pipe-friendly access of single elements:

```{r include = FALSE}
# Consistent pipe-friendly access of single elements
```
```{r 33-consistent-pipe-friendly-access-of-single-elements}
input_files %>%
  pluck(1)
input_files %>%
  pluck("berlin")
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. Explain the difference between `[` and `[[` subsetting.

1. Implement a variant of subsetting in "tibble-land" with a combination of `enframe()`, `slice()` or `filter()`, and `deframe()`:
    
    ```r
    input_files %>%
      enframe() %>% 
      ___(_____) %>% 
      deframe()
    ```
    
    ```{r echo = FALSE}
    input_files %>%
      enframe() %>% 
      filter(name == "toronto") %>% 
      deframe()
    ```
    
