```{r 34-remove-all, include = FALSE}
rm(list = ls())
```


## Construction

<details><summary>*Click here to show setup code.*</summary>
</details>

The `c()` function constructs vectors.
All elements of a vector must have the same type.

```{r include = FALSE}
### Construction

```
```{r 34-setup-05-construct-r}
c(1, 2, 3)
c(1:3, 5)
c(1:3, "5")
```

Lists are constructed with `list()`.
They are a special type of vector -- they can contain elements of different type and length.

```{r include = FALSE}
# Use list() to construct a list, all elements can have different types and lengths:
```
```{r 34-use-list-to-construct-a-list-all-elements-can-have-different-types-and-lengths}
list(1, 2, 3)
list(1:3, 5)
list(1:3, "5")
```

Lists can also contain other lists.

```{r include = FALSE}
# Lists can be nested:
```
```{r 34-lists-can-be-nested}
list(
  1:3,
  list(4, "5"),
  list(
    list(letters[6:8]),
    9
  )
)
```

Vectors (and also lists) can have names.

```{r include = FALSE}
# Vectors and lists can have names:
```
```{r 34-vectors-and-lists-can-have-names}
c(a = 1, b = 2, c = 3)
list(a = 1:3, b = 5)
set_names(1:3, letters[1:3])
```

The new {vctrs} package defines a data type for lists where all elements have the same type: a stricter list, but more powerful than a bare vector.

```{r include = FALSE}
# Preview: vctrs::list_of() to construct typed lists
```
```{r 34-preview-vctrs-list-of-to-construct-typed-lists}
#vctrs::list_of(1, 2, 3)
#vctrs::list_of(letters[1:3], "e")
```

```{r include = FALSE}
# Exercises
```

### Exercises

1. Explain the differences between the outputs below.

    ```{r echo = TRUE}
    c(a = list(1:3), b = list(4:5))
    list(a = list(1:3), b = list(4:5))
    ```
