```{r 34-remove-all, include = FALSE}
rm(list = ls())
```


## Pure functions and side effects

<!-- Setup 34-function-purity.R -->
```{r include = FALSE}
# Setup 34-function-purity.R
```
```{r 34-setup-34-function-purity-r}
library(tidyverse)
```

Functions should do one thing, and do it well.^[Unix philosophy, originated by Ken Thompson]

<!-- Functions should do one thing, and do it well. -->
```{r include = FALSE}
# Functions should do one thing, and do it well.
```
```{r 34-functions-should-do-one-thing-and-do-it-well}

```

Pure function: called for its return value, no side effects:

<!-- Pure function: called for its return value, no side effects! -->
```{r include = FALSE}
# Pure function: called for its return value, no side effects!
```
```{r 34-pure-function-called-for-its-return-value-no-side-effects}
pure_function <- function(x) {
  x + 1
}

pure_function(1)
```


<!-- Function with side effect: called for its side effect, returns input -->


Function with side effect: called for its side effect, returns input (here invisibly; assigning is possible):

<!-- invisibly (=no changes to return value). -->
```{r include = FALSE}
# Function with side effect: called for its side effect, returns input
# invisibly (=no changes to return value).
```
```{r 34-function-with-side-effect-called-for-its-side-effect-returns-input}
side_effect_function <- function(x) {
  file <- tempfile()
  writeLines(format(x), tempfile())
  print(x)
  message(x, " written to ", file)

  invisible(x)
}

side_effect_function(2)
```


Separation helps isolate the side effects. 
If side effect functions return the input, they remain composable with pure functions:



<!-- Separation helps isolate the side effects. -->
<!-- If side effect functions return the input, they remain composable with -->
<!-- pure functions. -->
```{r include = FALSE}
# Separation helps isolate the side effects.
# If side effect functions return the input, they remain composable with
# pure functions.
```
```{r 34-separation-helps-isolate-the-side-effects}
5 %>%
  pure_function() %>%
  side_effect_function() %>%
  pure_function()
```
