```{r 35-remove-all, include = FALSE}
rm(list = ls())
```


## Processing multiple files {#map}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Processing multiple files

```
```{r 35-setup-06-map-r}
library(tidyverse)
library(here)

dict <- readxl::read_excel(here("data/cities.xlsx"))

input_files <-
  dict %>%
  select(city_code, weather_filename) %>%
  deframe()
```
</details>

Here we look at how to act on each entry of a list or a vector using `purrr::map()`:

We start with the named vector `input_files` from section ["Indexing"](#indexing).
As just seen, manually choosing just one entry of a vector works like so:

```{r include = FALSE}
# Read a single input file
```
```{r 35-read-a-single-input-file}
readxl::read_excel(here(input_files[[1]]))
```

With `map()`, you can successively work through the whole vector and each time let the same function deal with the respective entry.
The output of `map()` is a list where each element contains one results.
The list is named if the input is named:

```{r include = FALSE}
# Read all input files
```
```{r 35-read-all-input-files}
input_data <-
  map(input_files, ~ readxl::read_excel(here(.)))
```

Let's take a closer look at what we produced:

```{r include = FALSE}
# Analyze the results
```
```{r 35-analyze-the-results}
input_data
input_data[[1]]
names(input_data)
```

`map()` can be included in your pipe in the following way:

```{r include = FALSE}
# Pipe notation
```
```{r 35-pipe-notation}
input_files %>%
  map(~ readxl::read_excel(here(.)))
```

```{r include = FALSE}
# Exercises
```

### Exercises

1. Read only the data for Toronto and Tel Aviv, using subsetting or `filter()`. Compare.

    ```r
    input_files[_____] %>% 
      map(~ readxl::read_excel(here(.)))

    input_files %>%
      ___() %>% 
      filter(name %in% c(_____)) %>% 
      ___() %>% 
      map(~ readxl::read_excel(here(.)))
    ```
    
    ```{r echo = FALSE}
    input_files[c("toronto", "tel_aviv")] %>% 
      map(~ readxl::read_excel(here(.)))

    input_files %>%
      enframe() %>% 
      filter(name %in% c("toronto", "tel_aviv")) %>% 
      deframe() %>% 
      map(~ readxl::read_excel(here(.)))
    ```

1. Compute the absolute file name with `here()` outside of the `map()` call.

    ```r
    input_files %>% 
      enframe() %>% 
      ___(_____) %>% 
      deframe() %>% 
      map(~ readxl::read_excel(.))
    ```

    ```{r echo = FALSE}
    input_files %>% 
      enframe() %>% 
      mutate(value = here(value)) %>% 
      deframe() %>% 
      map(~ readxl::read_excel(.))
    ```

1. Can you explain what happens when you call `enframe()` on the result? Can you explain?

    ```r
    input_files %>%
      map(~ readxl::read_excel(here(.))) %>% 
      enframe()
    ```
    
