```{r 36-remove-all, include = FALSE}
rm(list = ls())
```


## Argument matching

<details><summary>Setup code</summary>
```{r include = FALSE}
### Argument matching

```
```{r 36-setup-36-args-matching-r}

```
</details>


Named arguments are assigned first, after that remaining slots are filled from left to right.

```{r include = FALSE}
# Call matching
```
```{r 36-call-matching}
use_names <- function(a = 1, b = 2) {
  list(a = a, b = b)
}

use_names(3, 4)
use_names(a = 3, 4)
use_names(3, a = 4)
use_names(a = 3, b = 4)
```

The ellipsis can be used to enfore the user to name the function parameters when setting them:

```{r include = FALSE}
# The ellipsis is useful to enforce naming of arguments
```
```{r 36-the-ellipsis-is-useful-to-enforce-naming-of-arguments}
enforce_names <- function(..., a = 1, b = 2) {
  list(a = a, b = b)
}

enforce_names(3, 4)
enforce_names(a = 3, 4)
enforce_names(a = 3, b = 4)
```

Inside a function with an ellipsis as a parameter, you can capture the ellipsis with `list()`:

```{r include = FALSE}
# Arguments in ellipsis can be captured via list()
```
```{r 36-arguments-in-ellipsis-can-be-captured-via-list}
ellipsis_test <- function(...) {
  args <- list(...)
  names(args)
}

ellipsis_test(a = 1, 2, c = 3:5)
```


### Exercise

Naming, not naming or partly naming parameters in functions calls? What does the following return and why?

```{r include = FALSE}
## Exercise: call matching
```
```{r 36-exercise-call-matching}

```


```{r include = FALSE}
## Ellipsis inbetween
```
```{r 36-ellipsis-inbetween}


use_some_names <- function(a = 1, ..., b = 2) {
  list(a = a, b = b)
}

use_some_names(3, 4)
use_some_names(a = 3, 4)
use_some_names(3, a = 4)
use_some_names(a = 3, b = 4)
use_some_names(b = 4, 3)
```


```{r include = FALSE}
## Program defensively!
```
```{r 36-program-defensively}

use_always_names <- function(..., a = 1, b = 2) {
  extra_args <- list(...)
  stopifnot(length(extra_args) == 0)

  list(a = a, b = b)
}

try(use_always_names(3, 4))
try(use_always_names(a = 3, 4))
try(use_always_names(3, a = 4))
try(use_always_names(b = 4, 3))
use_always_names(a = 3, b = 4)
```
