```{r 36-remove-all, include = FALSE}
rm(list = ls())
```


## Manipulating all datasets {#map_manip}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Manipulating all datasets

```
```{r 36-setup-07-map-manip-r}
library(tidyverse)
library(here)

dict <- readxl::read_excel(here("data/cities.xlsx"))

input_data <-
  dict %>%
  select(city_code, weather_filename) %>%
  deframe() %>%
  map(~ readxl::read_excel(here(.)))
```
</details>

How to selectively manipulate specific parts of a list of datasets?

We start with the named list of tibbles called `input_data` from section ["Processing all files"](#map).
Of each tibble we only want the column `time` and all the columns whose name contains "emperature".
We test with the first entry:

```{r include = FALSE}
# Manipulate first result
```
```{r 36-manipulate-first-result}
input_data[[1]] %>%
  select(time, contains("emperature"))
```

To apply this on all entries, we use `map()` again.
Note that we need an explicit dot (`.`) in the `select()` call here, to indicate the position where each sub-dataset will be plugged in.

```{r include = FALSE}
# Manipulate results
```
```{r 36-manipulate-results}
input_data %>%
  map(~ select(., time, contains("emperature")))
```

We can extend this to preserve only the observations with `temperature` greater or equal than 14°C:

```{r include = FALSE}
# Manipulate results more
```
```{r 36-manipulate-results-more}
input_data %>%
  map(~ select(., time, contains("emperature"))) %>%
  map(~ filter(., temperature >= 14))
```

Create a custom function for that specific purpose in a call to `map()`:

```{r include = FALSE}
# Create a function to manipulate
```
```{r 36-create-a-function-to-manipulate}
manipulator <- function(data) {
  data %>%
    select(time, contains("emperature")) %>%
    filter(temperature >= 14)
}
```

Let's look at the object `manipulator`, that we created:

```{r include = FALSE}
# Functions are first-class objects!
```
```{r 36-functions-are-first-class-objects}
manipulator
```

See the ["Function basics"](#function-basics) chapter for a more extensive introduction to functions.

Testing the function:

```{r include = FALSE}
# Test the function
```
```{r 36-test-the-function}
manipulator(input_data[[4]])
```

Now let's use `map()` to let our function act on the entire dataset:

```{r include = FALSE}
# Run the function on the entire dataset
```
```{r 36-run-the-function-on-the-entire-dataset}
manipulated_data <- map(input_data, ~ manipulator(.))
manipulated_data
```

`map()` allows for the following shortcut notation for functions with one argument only:

```{r include = FALSE}
# Shortcut
```
```{r 36-shortcut}
map(input_data, manipulator)
```

```{r include = FALSE}
# Exercises
```

### Exercises

1. Use `summarize()` to compute the mean temperature and humidity for each city during that period.

    ```r
    input_data %>% 
      ___(~ ___(., mean(___), mean(___)))
    ```
    
    ```{r echo = FALSE}
    input_data %>% 
      map(~ summarize(., mean(temperature), mean(humidity)))
    ```

1. Create a function to compute the daily mean of these values for each dataset:

    ```r
    compute_daily_mean <- ___(data) {
      data %>%
        ___(as.Date(time)) %>%
        ___(_____) %>%
        ungroup()
    }
    input_data %>% 
      ___(___)
    ```
    
    ```{r echo = FALSE}
    compute_daily_mean <- function(data) {
      data %>% 
        group_by(as.Date(time)) %>% 
        summarize(mean(temperature), mean(humidity)) %>% 
        ungroup()
    }
    input_data %>% 
      map(compute_daily_mean)
    ```

1. Use the `dim()` function to compute the dimensions of each sub-dataset. Then, use `prod()` to compute the number of cells. Discuss your observation.

    ```r
    input_data %>% 
      _____
    input_data %>% 
      _____ %>% 
      _____
    ```
    
    ```{r echo = FALSE}
    input_data %>% 
      map(dim)
    input_data %>% 
      map(dim) %>% 
      map(prod)
    ```

1. Create four plots of humidity vs. pressure, one for each city. Use `geom_path()`, map `temperature` to the `color` aesthetic:

    ```r
    create_plot <- function(___) {
      ___ %>% 
        ggplot(aes(_____)) +
        geom_path()
    }
    ___ %>% 
      ___(___)
    ```
    
    ```{r echo = FALSE}
    create_plot <- function(data) {
      data %>% 
        ggplot(aes(x = pressure, y = humidity, color = temperature)) +
        geom_path()
    }
    input_data %>% 
      map(create_plot)
    ```
