```{r 37-remove-all, include = FALSE}
rm(list = ls())
```


## Typed output



<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Typed output

```
```{r 37-setup-08-map-type-r}
library(tidyverse)
library(here)

dict <- readxl::read_excel(here("data/cities.xlsx"))

input_data <-
  dict %>%
  select(city_code, weather_filename) %>%
  deframe() %>%
  map(~ readxl::read_excel(here(.)))
```
</details>

If we know, what the output of each function call in a `map()` sequence looks like, we can often call a sub-type of `map()` to produce a more condensed output.

We start with the named list of tibbles called `input_data` from section ["Processing all files"](#map).

We want to know the number of rows of each tibble in `input_data`:

```{r include = FALSE}
# map() returns a list
```
```{r 37-map-returns-a-list}
input_data %>%
  map(~ nrow(.))
```

Each time an integer is produced.
Therefore we can call `map_int()`, to create a named integer vector:

```{r include = FALSE}
# Return an integer vector with map_int()
```
```{r 37-return-an-integer-vector-with-map-int}
input_data %>%
  map_int(~ nrow(.))
```

If the output is a character variable, use `map_chr()`:

```{r include = FALSE}
# ... or a character vector?
```
```{r 37-or-a-character-vector}
input_data %>%
  map_chr(~ as.character(nrow(.)))
```

There are sub-types of the `map()` function for each atomic type:

- integer: `map_int()`

- numeric (double-precision value): `map_dbl()`

- character (strings): `map_chr()`

- logical (flags): `map_lgl()`

- raw (bytes): `map_raw()`

```{r include = FALSE}
# Exercises
```

### Exercises

1. Explain what happens if you try to use `map_dbl()` with the `dim()` output:

    ```r
    input_data %>% 
      map_dbl(dim)
    ```

1. Extract a concise version of the first temperature value for each dataset:

    ```r
    input_data %>% 
      map(~ slice(., 1)) %>%
      ___(~ pull(_____))
    ```
    
    ```{r echo = FALSE}
    input_data %>% 
      map(~ slice(., 1)) %>%
      map_dbl(~ pull(., temperature))
    ```

1. Use `paste0()` to build a textual description for the weather during the observed period in a function. Create a two-column tibble.

    ```r
    summarize_weather <- _____ {
      ___ %>%
        ___(
          _____,
          _____,
          _____,
          summary = paste(rle(summary)$values, collapse = ", then ")
        )
    }

    describe_weather <- function(weather_summary) {
      weather_summary %>%
        mutate(
          text = paste0(
            "We had temperatures between ", min_temp, " and ", max_temp, " °C.",
            "The average humidity was ", round(mean_humidity * 100), " %. ",
            "The weather was ", summary, "."
          )
        ) %>% 
        pull()
    }
    
    input_data %>% 
      ___(___) %>%
      ___(___) %>% 
      ___()
    ```
    
    ```{r echo = FALSE}
    summarize_weather <- function(data) {
      data %>%
        summarize(
          max_temp = max(temperature),
          min_temp = min(temperature),
          mean_humidity = mean(humidity),
          summary = paste(rle(summary)$values, collapse = ", then ")
        )
    }

    describe_weather <- function(weather_summary) {
      weather_summary %>%
        mutate(
          text = paste0(
            "We had temperatures between ", min_temp, " and ", max_temp, " °C.",
            "The average humidity was ", round(mean_humidity * 100), " %. ",
            "The weather was ", summary, "."
          )
        ) %>% 
        pull()
    }
    
    input_data %>% 
      map(summarize_weather) %>%
      map_chr(describe_weather) %>% 
      enframe()
    ```
