```{r 42-remove-all, include = FALSE}
rm(list = ls())
```


## Moving to tibble-land {#mut_map}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Moving to tibble-land

```
```{r 42-setup-42-mutate-map-r}
library(tidyverse)
library(here)

dict <- readxl::read_excel(here("data/cities.xlsx"))

input_data <-
  dict %>%
  select(city_code, weather_filename) %>%
  deframe() %>%
  map(~ readxl::read_excel(here(.)))
```
</details>

How to combine the abilities of `map()` & co., which work on vectors and lists, with our commonly used data structure, the tibble?

We start with the named list of tibbles called `input_data` from section ["Processing all files"](#map) and with `dict` from section ["Named vectors and two-column tibbles"](#names).

Calling `enframe()` to produce a data frame from `input_data` leads to a maybe at first surprising, but oftentimes useful result:

```{r include = FALSE}
# Lists are also vectors, enframe() returns a nested tibble!
```
```{r 42-lists-are-also-vectors-enframe-returns-a-nested-tibble}
nested_input_data <-
  input_data %>%
  enframe()

nested_input_data
```

This is because lists are also vectors.
In our case each list entry contains a tibble, which can be "nested" into each entry of column `value`.

Starting with the tibble `dict` we can see how `dpylr::mutate()` and `map()` can nicely work together to produce a somewhat similar result:

```{r include = FALSE}
# Operate in "tibble-land" right away: columns are vectors
```
```{r 42-operate-in-tibble-land-right-away-columns-are-vectors}
dict %>%
  select(city_code, weather_filename) %>%
  mutate(
    data = map(weather_filename, ~ readxl::read_excel(here(.)))
  )
```

This works because `R` interprets columns of tibbles as vectors, which can be fed to `map()`.
To simplify the `map()` call, we create an intermediate column:

```{r include = FALSE}
# Create an intermediate column to simplify the map() call:
```
```{r 42-create-an-intermediate-column-to-simplify-the-map-call}
dict %>%
  select(city_code, weather_filename) %>%
  mutate(path = here(weather_filename)) %>%
  mutate(data = map(path, readxl::read_excel))
```


Staying in "tibble-land" as long as possible helps retaining other important components of the data you are processing, so that you can keep using familiar data transformation tools.


```{r include = FALSE}
# Keep important columns
```
```{r 42-keep-important-columns}
dict_data <-
  dict %>%
  mutate(
    data = map(weather_filename, ~ readxl::read_excel(here(.))),
    rows = map_int(data, nrow),
  ) %>%
  select(-weather_filename)
dict_data
```

This pattern can also be used with the `map2()` family of functions:

```{r include = FALSE}
# Also with map2:
```
```{r 42-also-with-map-2}
dict_data_with_desc <-
  dict_data %>%
  mutate(
    desc = map2_chr(
      name, rows,
      ~ paste0(..2, " rows in data for ", ..1)
    )
  )
```

Because `mutate()` always appends to the end, the most recently added column can always be accessed with `pull()`:

```{r include = FALSE}
# Access the most recently added column with pull():
```
```{r 42-access-the-most-recently-added-column-with-pull}
dict_data_with_desc %>%
  pull()
```


More generally, `pmap()` supports functions with an arbitrary number of arguments:

```{r include = FALSE}
# More than two arguments:
```
```{r 42-more-than-two-arguments}
dict_data %>%
  mutate(
    cols = map_int(data, ncol),
    desc = pmap_chr(
      list(name, rows, cols),
      ~ paste0(..2, " rows and ", ..3, " cols in data for ", ..1)
    )
  )
```


```{r include = FALSE}
# A nicer interface?
```
```{r 42-a-nicer-interface, include = FALSE}
map_mutate <- function(.data, col, expr) {
  col <- rlang::enexpr(col)

  .data %>%
    mutate(data = map(!!col, expr))
}

dict %>%
  map_mutate(weather_filename, ~ readxl::read_excel(here(.)))
```


```{r include = FALSE}
# Process a tibble rowwise: an alternative
```
```{r 42-process-a-tibble-rowwise-an-alternative, include = FALSE}
processor <- function(row) {
  row %>%
    mutate(cells = prod(dim(data[[1]])))
}

dict_data %>%
  rowid_to_column() %>%
  nest(-rowid) %>%
  pull() %>%
  map(processor) %>%
  bind_rows()
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. The `imap()` family of functions iterates over a vector and its names:

    ```{r}
    input_data %>% 
      imap_chr(~ paste0(.y, ": ", nrow(.x), " rows"))
    ```
    
    Implement the same functionality using `map2()` inside a `mutate()`, and `enframe()`:

    ```r
    manipulated_data %>%
      ___() %>%
      mutate(___ = map2()) %>%
      deframe()
    ```
