```{r 43-remove-all, include = FALSE}
rm(list = ls())
```


## Scope

When working with functions, it is important to be aware of the scope of objects, i.e. what is known in which context?

```{r include = FALSE}
### Scope

```
```{r 43-setup-43-function-scoping-r}
a <- 5
```

`a` is now an object of the global environemnt. A function can access global variables:

```{r include = FALSE}
# A function can access global variables:
```
```{r 43-a-function-can-access-global-variables}
f <- function() {
  a
}

f()
```

On the other hand, a variable which is defined inside a function, will not be known outside of that function. Respectively, it won't overwrite the value of global variables.

```{r include = FALSE}
# When a function writes to a variable, it always writes in scope
```
```{r 43-when-a-function-writes-to-a-variable-it-always-writes-in-scope}
f <- function() {
  a <- 2
  a
}

f()
a
```


Global variables are a (hidden) part of a function's interface.
Best practice: functions should be self-contained, independent of global variables.

```{r include = FALSE}
# Global variables are a (hidden) part of a function's interface!
# Best practice: self-contained functions, independent of global variables
```
```{r 43-global-variables-are-a-hidden-part-of-a-function-s-interface}

```


```{r include = FALSE}
## Exercises:
```
```{r 43-exercises}
```
