```{r 43-remove-all, include = FALSE}
rm(list = ls())
```


## Nesting and unnesting {#nest}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Nesting and unnesting

```
```{r 43-setup-13-unnest-r}
library(tidyverse)
library(here)

dict <- readxl::read_excel(here("data/cities.xlsx"))

dict_data <-
  dict %>%
  mutate(data = map(weather_filename, ~ readxl::read_excel(here(.)))) %>%
  select(-weather_filename)
```
</details>

How to work with nested data?

We start with the tibble `dict_data` from section ["Moving to tibble-land"](#mut_map), which includes the nested tibbles in its column `data`.

If we want to actually look at the data we can directly use `tidyr::unnest()` on the whole tibble, which by default acts on all list-columns.
This blows up our tibble by repeating the formerly unnested column entries as many times, as each nested tibble has rows:

```{r include = FALSE}
# Flatten a nested tibble with unnest():
```
```{r 43-flatten-a-nested-tibble-with-unnest}
dict_data %>%
  unnest()

dict_data %>%
  unnest() %>%
  count(name)
```

Inversely, if you want to have a more condensed view of your data, you can nest again.
By default, the function `tidyr::nest()` will nest all data.
Therefore it is often useful to tell it, which columns to ignore:

```{r include = FALSE}
# Inverse operation: nest()
```
```{r 43-inverse-operation-nest}
dict_data %>%
  unnest() %>%
  nest(-city_code, -name, -lng, -lat)
```

Using this, we structure our data in new, customized ways.
Here, we create a new column `date`, by dropping the detailed information of the time of the day, and create a nested tibble for each day:

```{r include = FALSE}
# Split into daily data:
```
```{r 43-split-into-daily-data}
dict_data %>%
  unnest() %>%
  mutate(date = as.Date(time)) %>%
  nest(-date)
```
