```{r 51-remove-all, include = FALSE}
rm(list = ls())
```

```{r include = FALSE}
### Scope

```
```{r 51-setup-51-function-scoping-r}
```

## Scope

What happens if a function defines variables that have a variable by the same name in the global environment?

We start with a variable defined in the global environment:

```{r include = FALSE}
# Define global variable
```
```{r 51-init}
a <- 5
```

A function can access global variables:

```{r include = FALSE}
# A function can access global variables:
```
```{r 51-a-function-can-access-global-variables}
f <- function() {
  a
}

f()
```

On the other hand, a variable which is defined inside a function is contained in that function.
It will not be known outside of that function.
Respectively, it won't overwrite the value of global variables.

```{r include = FALSE}
# When a function writes to a variable, it always writes in scope
```
```{r 51-when-a-function-writes-to-a-variable-it-always-writes-in-scope}
f <- function() {
  a <- 2
  a
}

f()
a
```


Global variables are a (hidden) part of a function's interface.
Ideally, functions are be self-contained, independent of global variables.
Notable exceptions are objects are used across your entire analysis, such as "the dataset".
(Otherwise you would need to pass them across many layers.)

```{r include = FALSE}
# Global variables are a (hidden) part of a function's interface!
# Best practice: self-contained functions, independent of global variables
```
```{r 51-global-variables-are-a-hidden-part-of-a-function-s-interface}

```


```{r include = FALSE}
# Exercises
```

### Exercises

1. Double-check what happens if two functions declare/use a variable of the same name.
    
    ```{r results = "hide"}
    # Variables in different functions
    f1 <- function() {
      a <- 3
      a + f2()
    }

    f2 <- function() {
      a
    }
    
    f1()
    f2()
    a
    ```
