```{r 51-remove-all, include = FALSE}
rm(list = ls())
```


## Control flow

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Control flow

```
```{r 51-setup-51-function-if-r}
library(tidyverse)
library(here)

weather_path <- function(filename) {
  # Returned value
  here("data/weather", filename)
}
read_weather_file <- function(filename) {
  readxl::read_excel(weather_path(filename))
}
```
</details>

We start once more with the functions `weather_path()` from section ["Arguments"](#args) and `read_weather_file()` from section ["Intermediate variables"](#intermediate).

A way to regulate the control flow is by using `if ()`:

```{r include = FALSE}
# if () executes code conditionally
```
```{r 51-if-executes-code-conditionally}
read_weather_data <- function(omit_zurich = FALSE, omit_toronto = FALSE) {
  # Create ensemble dataset from files on disk
  weather_data <- bind_rows(
    berlin = read_weather_file("berlin.xlsx"),
    toronto = read_weather_file("toronto.xlsx"),
    tel_aviv = read_weather_file("tel_aviv.xlsx"),
    zurich = read_weather_file("zurich.xlsx"),
    .id = "city_code"
  )

  # Filter, conditionally
  if (omit_zurich) {
    weather_data <-
      weather_data %>%
      filter(city_code != "zurich")
  }

  if (omit_toronto) {
    weather_data <-
      weather_data %>%
      filter(city_code != "toronto")
  }

  # Return result
  weather_data
}

read_weather_data(omit_toronto = TRUE, omit_zurich = TRUE) %>%
  count(city_code)

read_weather_data(omit_toronto = TRUE, omit_zurich = FALSE) %>%
  count(city_code)
```




This can be useful if aiming at a possible early return:

```{r include = FALSE}
# Useful with an early return()
# && and ||: shortcut operators for scalar logical
```
```{r 51-useful-with-an-early-return}
read_weather_data <- function(omit_zurich = FALSE, omit_toronto = FALSE) {
  # Create ensemble dataset from files on disk
  weather_data <- bind_rows(
    berlin = read_weather_file("berlin.xlsx"),
    toronto = read_weather_file("toronto.xlsx"),
    tel_aviv = read_weather_file("tel_aviv.xlsx"),
    zurich = read_weather_file("zurich.xlsx"),
    .id = "city_code"
  )

  # Can keep original data?
  if (!omit_zurich && !omit_toronto) {
    return(weather_data)
  }

  # Filter, conditionally
  if (omit_zurich) {
    weather_data <-
      weather_data %>%
      filter(city_code != "zurich")
  }

  if (omit_toronto) {
    weather_data <-
      weather_data %>%
      filter(city_code != "toronto")
  }

  # Return result
  weather_data
}
```


Conditional branching with if-else-logic. 
(This is just for illustration, you should not implement code like this!)

```{r include = FALSE}
# else if/else: branching
# (Just for illustration, do not implement code like this!)
```
```{r 51-else-if-else-branching}
read_weather_data <- function(omit_zurich = FALSE, omit_toronto = FALSE) {
  # Create ensemble dataset from files on disk
  weather_data <- bind_rows(
    berlin = read_weather_file("berlin.xlsx"),
    toronto = read_weather_file("toronto.xlsx"),
    tel_aviv = read_weather_file("tel_aviv.xlsx"),
    zurich = read_weather_file("zurich.xlsx"),
    .id = "city_code"
  )

  # Filter, conditionally, and return
  if (!omit_zurich && !omit_toronto) {
    weather_data
  } else if (omit_zurich && !omit_toronto) {
    weather_data %>%
      filter(city_code != "zurich")
  } else if (!omit_zurich && omit_toronto) {
    weather_data %>%
      filter(city_code != "toronto")
  } else {
    # Filter both
    weather_data %>%
      filter(city_code != "zurich") %>%
      filter(city_code != "toronto")
  }
}

read_weather_data(omit_toronto = TRUE) %>%
  count(city_code)
read_weather_data(omit_zurich = TRUE) %>%
  count(city_code)
```
