```{r 52-remove-all, include = FALSE}
rm(list = ls())
```


## Pure functions and side effects

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Pure functions and side effects

```
```{r 52-setup-44-function-purity-r}
library(tidyverse)
```
</details>

Functions should do one thing, and do it well.^[Unix philosophy, originated by Ken Thompson]

```{r include = FALSE}
# Functions should do one thing, and do it well.
```
```{r 52-functions-should-do-one-thing-and-do-it-well}

```

A *pure function* is one that is called for its return value and which has no side effects:

```{r include = FALSE}
# Pure function: called for its return value, no side effects!
```
```{r 52-pure-function-called-for-its-return-value-no-side-effects}
pure_function <- function(x) {
  x + 1
}

pure_function(1)
```

For functions with side effect, it is good practice to return the input invisibly:

```{r include = FALSE}
# Function with side effect: called for its side effect, returns input
# invisibly (=no changes to return value).
```
```{r 52-function-with-side-effect-called-for-its-side-effect-returns-input}
side_effect_function <- function(x) {
  file <- tempfile()
  writeLines(format(x), tempfile())
  print(x)
  message(x, " written to ", file)

  invisible(x)
}

side_effect_function(2)
```


Separation helps isolate the side effects.
If side effect functions return the input, they remain composable with pure functions:



```{r include = FALSE}
# Separation helps isolate the side effects.
# If side effect functions return the input, they remain composable with
# pure functions.
```
```{r 52-separation-helps-isolate-the-side-effects}
5 %>%
  pure_function() %>%
  side_effect_function() %>%
  pure_function()
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. In the above example, which part of the pipe triggers the display of `6` and `7`, respectively?

1. How do you create a function that returns more than one value?

1. Implement your own purely functional version of `sum()` by using `reduce()`. (Hint: `` `+` `` is a function that takes two arguments and returns the sum.)
    
    ```r
    reduce(1:5, ___)
    ```
    ```{r echo = FALSE}
    reduce(1:5, `+`)
    ```

1. Implement your own purely functional version of `cumsum()` by using `accumulate()`. 

    ```r
    accumulate(1:5, ___)
    ```
    ```{r echo = FALSE}
    accumulate(1:5, `+`)
    ```

1. Implement your own purely functional version of `cumsum()` by using `reduce()` only. (Hint: Use `tail(., 1)` to access the last element of a vector.)

    ```r
    reduce(1:5, ~ _____)
    ```
    ```{r echo = FALSE}
    reduce(1:5, ~ c(..1, tail(..1, 1) + ..2))
    ```
