```{r 54-remove-all, include = FALSE}
rm(list = ls())
```


## Closures

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Closures

```
```{r 54-setup-54-closure-r}
library(tidyverse)
library(here)

weather_path <- function(filename) {
  # Returned value
  here("data/weather", filename)
}

read_weather_file <- function(filename) {
  readxl::read_excel(weather_path(filename))
}

get_weather_file_for <- function(city_code) {
  paste0(city_code, ".xlsx")
}

get_weather_data_for <- function(city_code) {
  read_weather_file(get_weather_file_for(city_code))
}
```
</details>

Closures can e.g. be used during function definition. 

We start once more with the functions `weather_path()` from section ["Arguments"](#args) and `read_weather_file()` from section ["Intermediate variables"](#intermediate).

Here we create a function that loads a particular dataset:

```{r include = FALSE}
# Create a function that loads a particular dataset
```
```{r 54-create-a-function-that-loads-a-particular-dataset}
make_read_weather_file <- function(filename) {
  # Avoid odd effects due to lazy evaluation
  force(filename)

  # This function (closure) accesses the filename from the
  # outer function
  f <- function() {
    read_weather_file(filename)
  }

  f
}

read_berlin <- make_read_weather_file("berlin.xlsx")
read_toronto <- make_read_weather_file("toronto.xlsx")
read_tel_aviv <- make_read_weather_file("tel_aviv.xlsx")
read_zurich <- make_read_weather_file("zurich.xlsx")

read_berlin
read_toronto

read_berlin()
read_toronto()
```

Use closures as wrappers for other verbs/functions (such functions are also called "adverbs"):

```{r include = FALSE}
# Use case: adverbs -- wrappers for other verbs
```
```{r 54-use-case-adverbs-wrappers-for-other-verbs}
loudly <- function(f) {
  force(f)

  function(...) {
    args <- list(...)
    msg <- paste0(length(args), " argument(s)")
    message(msg)

    f(...)
  }
}

read_loudly <- loudly(read_weather_file)
read_loudly
read_loudly("berlin.xlsx")
```

The `safely()` function is another example from the purrr package:

```{r include = FALSE}
# safely()
```
```{r 54-safely}
cities <- list("berlin", "toronto", "milan", "tel_aviv")
try(map(cities, get_weather_data_for))
map(cities, safely(get_weather_data_for))
safely(get_weather_data_for)

map(cities, ~ safely(get_weather_data_for)(.))

safe_get_weather_data_for <- safely(get_weather_data_for)
map(cities, ~ safe_get_weather_data_for(.))
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. Review the help and the implementation of `safely()` and `possibly()`.
    
    ```{r}
    safely
    possibly
    ```
