```{r 61-remove-all, include = FALSE}
rm(list = ls())
```


## Traversing {#berlin}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Traversing

```
```{r 61-setup-61-berlin-r}
library(tidyverse)
library(here)
```
</details>

We are now working with the results from downloading geolocation data from [photon.komoot.de](http://photon.komoot.de/).
This is stored in the file `here("data/komoot-berlin.rds")` and we can read it with `readRDS()`:

```{r include = FALSE}
# Results from downloading geolocation data from photon.komoot.de:
```
```{r 61-results-from-downloading-geolocation-data-from-photon-komoot-de}
berlin <- readRDS(here("data/komoot-berlin.rds"))

berlin
str(berlin)
```

As you can see it is a somewhat complex list structure.
We know from ["Indexing"](#indexing) that we can access it's components in the following way:

```{r include = FALSE}
# Access components
```
```{r 61-access-components}
berlin$type
berlin$features
berlin$features[[1]]
```

With the function `purrr::pluck()`, there is however a more universal tool available for accessing elements of more complex lists:

```{r include = FALSE}
# Uniform access with pluck():
```
```{r 61-uniform-access-with-pluck}
berlin %>%
  pluck("type")
berlin[["type"]]

berlin %>%
  pluck("features")

berlin %>%
  pluck("features", 1)
berlin[["features"]][[1]]

berlin %>%
  pluck("features", 1, "geometry")
berlin[["features"]][[1]][["geometry"]]

berlin %>%
  pluck("features", 1, "geometry", "coordinates")
```

Similarly:

```{r include = FALSE}
# Accessing different properties
```
```{r 61-accessing-different-properties}
berlin %>%
  pluck("features", 1, "properties", "country")
```

And as one more important characteristic of a `tidyverse`-function, `pluck()` is pipe-able:

```{r include = FALSE}
# Composable
```
```{r 61-composable}
berlin %>%
  pluck("features", 1) %>%
  pluck("properties", "country")
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. Introduce a variable for the first feature. Collect the coordinates, the country and the postal code.
        
    ```r
    first_feature <-
      berlin %>% 
      ___(_____)
    
    first_feature %>% 
      ___(_____)
    
    first_feature %>% 
      ___(_____)
    
    first_feature %>% 
      ___(_____)
    ```
    
    ```{r echo = FALSE}
    first_feature <-
      berlin %>% 
      pluck("features", 1)
    first_feature %>% 
      pluck("coordinates")
    first_feature %>% 
      pluck("properties", "country")
    first_feature %>% 
      pluck("properties", "postcode")
    ```
