```{r 62-remove-all, include = FALSE}
rm(list = ls())
```


## Iterating and traversing {#komoot}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Iterating and traversing

```
```{r 62-setup-62-komoot-r}
library(tidyverse)
library(here)
```
</details>

Now we are not only working with the geolocation data for Berlin, but we are adding data for our usual suspects:

```{r include = FALSE}
# Results from downloading geolocation data for all cities from photon.komoot.de:
```
```{r 62-results-from-downloading-geolocation-data-for-all-cities-from-photon-komoot-de}
komoot <- readRDS(here("data/komoot.rds"))

komoot
```

It looks slightly different from the list `berlin` from section ["Traversing"](#berlin).
That is because we have the list-of-2 stored for each city in the column `content`.
By using `pull()` on `content`,  we can produce a list containing the information for all cities:

```{r include = FALSE}
# Results are stored in the "content" column:
```
```{r 62-results-are-stored-in-the-content-column}
komoot_content <-
  komoot %>%
  pull(content)

berlin <-
  komoot_content %>%
  pluck(1)

berlin %>%
  pluck("features", 1, "geometry", "coordinates")

toronto <-
  komoot_content %>%
  pluck(2)

toronto %>%
  pluck("features", 1, "geometry", "coordinates")
```

With `map()` we can access the same element of the respective list for each city:

```{r include = FALSE}
# Apply same pluck() on all values with map():
```
```{r 62-apply-same-pluck-on-all-values-with-map}
komoot_content %>%
  map(~ pluck(., "features", 1, "geometry", "coordinates"))
```

With `map()` we can also use a shorthand notation for this, without the need to use `pluck()`.
We can just give it a list of the arguments which we would normally use as arguments for `pluck()`:

```{r include = FALSE}
# Shortcut:
```
```{r 62-shortcut}
komoot_content %>%
  map(list("features", 1, "geometry", "coordinates"))
```

The access path can also be stored in a variable:


```{r include = FALSE}
# Can also be stored in a variable:
```
```{r 62-can-also-be-stored-in-a-variable}
accessor <- list("features", 1, "geometry", "coordinates")
coordinates <-
  komoot_content %>%
  map(accessor)
coordinates
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. Augment `komoot` with a columns containing information on the first feature only.
    
    ```{r echo = FALSE}
    komoot_first <- 
      komoot %>% 
      mutate(
        first_feature = map(content, list("features", 1))
      )
    komoot_first
    ```

1. Augment `komoot_first` with columns containing information on coordinates, place and postal code. Use accessors and appropriate types for the columns.
    
    ```r
    acc_coordinates <- _____
    acc_country <- _____
    komoot_first %>% 
      mutate(
        coordinates = ___(___, acc_coordinates),
        country = _____,
        postcode = map_chr(_____, ~ pluck(___, .default = NA))
      )
    ```

    ```{r echo = FALSE}
    acc_coordinates <- list("coordinates")
    acc_country <- list("properties", "country")
    komoot_first %>% 
      mutate(
        coordinates = map(first_feature, acc_coordinates),
        country = map_chr(first_feature, acc_country),
        postcode = map_chr(first_feature, ~ pluck(., "properties", "postcode", .default = NA))
      )
    ```
