```{r 63-remove-all, include = FALSE}
rm(list = ls())
```


## Plucking multiple locations {#multipluck}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Plucking multiple locations

```
```{r 63-setup-73-multi-r}
library(tidyverse)
library(here)

komoot <- readRDS(here("data/komoot.rds"))
komoot_content <-
  komoot %>%
  pull(content)
```
</details>

What if we want to access two different pieces of information of each main list point at once?

We are again starting in the setup with the list `komoot_content` from ["Iterating and traversing"](#komoot).

Let's define the two locations of the city-lists we would like to access:

```{r include = FALSE}
# Use multiple accessors:
```
```{r 63-use-multiple-accessors}
accessor_coords <- list("features", 1, "geometry", "coordinates")

komoot_content %>%
  map(accessor_coords)

accessor_country <- list("features", 1, "properties", "country")
komoot_content %>%
  map(accessor_country)
```

Combine them as a list of lists and hand it over to a `map()` inside a `map()`:

```{r include = FALSE}
# All at once:
```
```{r 63-all-at-once}
accessors <- list(coords = accessor_coords, country = accessor_country)

accessors %>%
  map(~ map(komoot_content, .))
```
