```{r 74-remove-all, include = FALSE}
rm(list = ls())
```


## Flattening {#flatten}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Flattening

```
```{r 74-setup-73-flatten-r}
library(tidyverse)
library(here)

komoot <- readRDS(here("data/komoot.rds"))

komoot_content <-
  komoot %>%
  pull(content)

coordinates <-
  komoot_content %>%
  map(list("features", 1, "geometry", "coordinates"))
```
</details>

It can occur that we end up with lists which are unnecessarily deep and we would like to make them flatter to make it easier to handle them.

We are starting in our setup with `komoot_content` and `coordinates` from section ["Iterating and traversing"](#komoot).

An example for an list that seems a bit too deep is given here:

```{r include = FALSE}
# Odd structure:
```
```{r 74-odd-structure}
coordinates %>%
  pluck(1)
```

We can chop off a layer of a list and end up with a vector with one of the functions `purrr::flatten_*()`. 
In the `*` we need to specify what class the output will be:

```{r include = FALSE}
# Flattening can chop off a layer, need to specify output type:
```
```{r 74-flattening-can-chop-off-a-layer-need-to-specify-output-type}
coordinates %>%
  pluck(1) %>%
  flatten_dbl()
```

Let's use `map()` to apply this to the entire list of our cities' coordinates:

```{r include = FALSE}
# Apply to entire list:
```
```{r 74-apply-to-entire-list}
coordinates %>%
  map(~ flatten_dbl(.))
```
