```{r 65-remove-all, include = FALSE}
rm(list = ls())
```


## Transposing {#transpose}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Transposing

```
```{r 65-setup-74-transpose-r}
library(tidyverse)
library(here)

komoot <- readRDS(here("data/komoot.rds"))

komoot_content <-
  komoot %>%
  pull(content)

coordinates <-
  komoot_content %>%
  map(list("features", 1, "geometry", "coordinates"))
```
</details>

You might know the mathematical concept of transposition from your linear algebra courses.
A similar concept is available in `R` when we are dealing with lists.

We are starting in our setup with `komoot_content` and `coordinates` from section ["Iterating and traversing"](#komoot).

Let's apply `purrr::transpose()` to our list `coordinates`:

```{r include = FALSE}
# Transposing inside out:
```
```{r 65-transposing-inside-out}
coordinates %>%
  transpose()
```

What was originally a list with 4 elements of which each one was a list of 2 elements has become a list of 2 elements of which each one is a list of 4 elements.
With `flatten_dbl()` we can simplify the structure, so that we end up with a list of 2, where each element consists of a vector of 4.
The first vector contains the longitude and the second the latitude of our cities:

```{r include = FALSE}
# Flatten to simplify structure:
```
```{r 65-flatten-to-simplify-structure}
coordinates_transposed <-
  coordinates %>%
  transpose() %>%
  map(~ flatten_dbl(.))
```


```{r include = FALSE}
# Exercises
```

### Exercises

1. Explain what happens if you transpose a tibble:

    ```r
    komoot %>%
      transpose()
    ```
