```{r 66-remove-all, include = FALSE}
rm(list = ls())
```


## Rectangling {#rectangulate}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Rectangling

```
```{r 66-setup-66-rectangulate-r}
library(tidyverse)
library(here)

komoot <- readRDS(here("data/komoot.rds"))

komoot_content <-
  komoot %>%
  pull(content)

coordinates_transposed <-
  komoot_content %>%
  map(list("features", 1, "geometry", "coordinates")) %>%
  transpose() %>%
  map(~ flatten_dbl(.))
```
</details>
Most of us `R`-users feel most at ease when dealing in `R` with data frames on which we can use a plethora of well-known (by us) functions with non-startling behaviour.
What if we don't get our data in such a form?

We are starting in our setup with the list `coordinates_transposed` from section ["Transposing"](#transpose).

A tibble is internally a list of named vectors of equal length.
In two easy steps we can therefore make a tibble out of the unnamed list `coordinates_transposed`:
```{r include = FALSE}
# A tibble is internally a list of named vectors of equal length:
```
```{r 66-a-tibble-is-internally-a-list-of-named-vectors-of-equal-length}
coordinates_transposed %>%
  rlang::set_names(c("lon", "lat"))

coordinates_transposed %>%
  rlang::set_names(c("lon", "lat")) %>%
  as_tibble()
```

If you want to keep the names open for now, but still get a tibble, you can set `as_tibble()`'s argument `.name_repair = "universal"`:

```{r include = FALSE}
# Name repair helps if you don't know the names yet
```
```{r 66-name-repair-helps-if-you-don-t-know-the-names-yet}
coordinates_transposed %>%
  as_tibble(.name_repair = "universal")

coordinates_transposed %>%
  as_tibble(.name_repair = "universal") %>%
  rename(lon = ...1, lat = ...2)
```
