```{r 67-remove-all, include = FALSE}
rm(list = ls())
```


## Accessing APIs

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Accessing APIs

```
```{r 67-setup-67-json-r}
library(tidyverse)
library(here)
```
</details>

When dealing with web-APIs, query results come frequently in the JSON (**J**ava**S**cript **O**bject **N**otation) format.
How to deal with this in R?
A way to "talk" with APIs is provided by the package {httr}.
The "GET"-query is executed by using `httr::GET()` with the URL, containing the query specifics, as an argument:
```{r include = FALSE}
# Use httr::GET() for GET requests:
```
```{r 67-use-httr-get-for-get-requests}
req <- httr::GET("https://photon.komoot.de/api/?q=Paradeplatz&limit=3")
```

If you are using this command in a script, you might want to make sure the following command is only executed once the query is finished processing:
```{r include = FALSE}
# Wait for the request to be processed:
```
```{r 67-wait-for-the-request-to-be-processed}
httr::stop_for_status(req)
```

The result of the query can be accessed via `httr::content()`:
```{r include = FALSE}
# Read the response:
```
```{r 67-read-the-response}
content <- httr::content(req)
content
```

As you can see, the result, as it is displayed in R, is already a nested list at this point.
And we now how to deal with these objects.

The object did originally come as a JSON object though, which you can see, if you look at the literal result of the query like so:
```{r include = FALSE}
# Display the original response:
```
```{r 67-display-the-original-response}
text_content <- httr::content(req, as = "text")
cat(text_content)
```

The package {jsonlite} has the function `jsonlite::prettify()` to offer, in order to display a one-line JSON-structure in a more clearly laid-out manner:
```{r include = FALSE}
# Pretty-print the original response:
```
```{r 67-pretty-print-the-original-response}
cat(jsonlite::prettify(text_content))
```
