```{r 71-remove-all, include = FALSE}
rm(list = ls())
```


## A custom plotting function {#colname}

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### A custom plotting function

```
```{r 71-setup-71-colname-r}
library(tidyverse)
library(rlang)
```
</details>

Knowledge of tidy evaluation can become necessary when creating own functions in the framework of the tidyverse.

Let's try to build a function that takes a data frame and an unquoted column name and produces a histogram from this column.
A naive approach would be the following function definition:

```{r include = FALSE}
# First attempt: create a function that plots a histogram,
# taking a variable name as input
```
```{r 71-first-attempt-create-a-function-that-plots-a-histogram}
tidy_histogram <- function(.data, x) {
  .data %>%
    ggplot(aes(x = x)) +
    geom_histogram()
}
```

Let's test this function in an easy setting:

```{r include = FALSE}
# Would that work?
```
```{r 71-would-that-work}
data <- tibble(a = 1:10)

try(print(
  data %>%
    tidy_histogram(a)
))

try(print(
  data %>%
    tidy_histogram("a")
))
```

Neither the first nor the second attempt worked. What went wrong?

If we add another column called `x`, it suddenly works:

```{r include = FALSE}
# No, the function is looking for a variable named x,
# no matter what we pass in:
```
```{r 71-no-the-function-is-looking-for-a-variable-named-x}
data <- tibble(a = 1:10, x = 11:20)

data %>%
  tidy_histogram(a)
```

The reason for it is, that our function is hard-coded to display a variable called `x`.
The problem lies in the code-snippet `aes(x = x)`.

In the tidyverse the solution for avoiding these ambiguities is by using expressions to capture the meaning (here: user input) of an unquoted variable and subsequently the bang-bang-operator (written in the code as `!!`; also called "unquote") to access/pass on this meaning at the right place.

In our example we do the following:

```{r include = FALSE}
# Solution: quote-unquote
```
```{r 71-solution-quote-unquote}
tidy_histogram <- function(.data, x) {
  # Treat the argument as a variable name
  expr <- enquo(x)

  .data %>%
    # Tell ggplot2 that expr *contains* the name of the variable,
    # instead of expecting a variable named `expr`
    ggplot(aes(x = !!expr)) +
    geom_histogram()
}

data %>%
  tidy_histogram(a)

data %>%
  tidy_histogram(x)

try(print(
  data %>%
    tidy_histogram(y)
))
```

But this behavior is different from our usual base-R usage of variables in functions.
How do some functions behave this way and others another way?
Let's have a look at how the 'problematic' tidyverse function `aes()` is implemented:

```{r include = FALSE}
# This requires tidyeval support from the function that is called!
```
```{r 71-this-requires-tidyeval-support-from-the-function-that-is-called}
aes
```

The reason for the behavior seen above is that the function itself makes use of capturing user input as an expression.
In this case it uses the function `enquos()`, which captures one or more expressions along with an unique identifier for the environment in which they are supposed to be evaluated eventually.
The default is to evaluate an expression ("standard evaluation").
With `enquo()` and `enquos()` the expressions that correspond to user input are captured.

```{r include = FALSE}
# Exercises
```
```{r 71-exercises}

```

As an example of a newly-built function in the tidyverse, here is a function that combines the functionalities of `dplyr::mutate()` and `purrr::map_dbl()`.
It takes as arguments a data frame, the column it is supposed to act upon and the function call it is supposed to use on each of the columns values:

```{r include = FALSE}
# mutate_map_dbl() function
```
```{r 71-mutate-map-dbl-function}
mutate_map_dbl <- function(.data, col, expr) {
  quo <- enquo(col)

  .data %>%
    mutate(new_column = map_dbl(!!quo, expr))
}

iris_nested <-
  iris %>%
  nest(-Species)

iris_nested %>%
  mutate_map_dbl(data, ~ mean(.$Petal.Width))
```
