```{r 72-remove-all, include = FALSE}
rm(list = ls())
```


## Do you need tidy evaluation?

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Do you need tidy evaluation?

```
```{r 72-setup-72-forward-r}
library(tidyverse)
```
</details>

So does everyone who wants to create any functions in the framework of the tidyverse need deep knowledge about tidy evaluation?

The answer is, it depends: often enough, you can avoid the need for this knowledge.
In the following example, which is a slight extension of `dplyr::summarize()`, you do not need to capture any expressions.
The function takes a data frame and an ellipsis.
And the ellipsis can be directly passed on to a tidyverse function (buzzphrase: "pass the dots").

```{r include = FALSE}
# Implement a version of summarize() that ungroups:
```
```{r 72-implement-a-version-of-summarize-that-ungroups}
summarize_ungroup <- function(.data, ...) {
  .data %>%
    summarize(...) %>%
    ungroup()
}
```

The function does what it promised to do:

```{r include = FALSE}
# Test it:
```
```{r 72-test-it}
mean_airtime_per_day <-
  nycflights13::flights %>%
  group_by(year, month, day) %>%
  summarize_ungroup(mean(air_time, na.rm = TRUE))

mean_airtime_per_day

mean_airtime_per_day %>%
  groups()
```
