```{r 73-remove-all, include = FALSE}
rm(list = ls())
```


## Explicit quote-unquote of ellipsis

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Explicit quote-unquote of ellipsis

```
```{r 73-setup-73-enquos-r}
library(tidyverse)
library(rlang)
```
</details>

There are cases though, when you need knowledge about what the user added to the ellipsis.
This is then handled by capturing the content in a list of quosures, which can be unquoted by the `!!!`-operator.
You need the "triple-bang" operator here, because the ellipsis can hold more than one expression.
`!!!` does two things: it unquotes the content and splices it into the current call.

We can practice this with our little new tidyverse function `summarize_ungroup()`:

```{r include = FALSE}
# Explicit capturing with enquos():
```
```{r 73-explicit-capturing-with-enquos}
summarize_ungroup <- function(.data, ...) {
  # Capture (quote) with enquos()
  quos <- enquos(...)

  # Use (unquote-splice) with !!!
  .data %>%
    summarize(!!!quos) %>%
    ungroup()
}
```

We didn't need to process the content, but it still works, as we can see here:

```{r include = FALSE}
# Test it:
```
```{r 73-test-it}
mean_airtime_per_day <-
  nycflights13::flights %>%
  group_by(year, month, day) %>%
  summarize_ungroup(mean(air_time, na.rm = TRUE))

mean_airtime_per_day

mean_airtime_per_day %>%
  groups()
```

To come back to our original example: `aes()` uses exactly this "quote-unquote-splice"-pattern:

```{r include = FALSE}
# aes() does the same:
# (summarize() did not at the time of writing: https://github.com/tidyverse/dplyr/pull/4357)
```
```{r 73-aes-does-the-same}
aes
```

At the time of producing the material for this course, `summarize()` did not make use of this pattern.
