```{r 74-remove-all, include = FALSE}
rm(list = ls())
```


## Names

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Names

```
```{r 74-setup-74-named-r}
library(tidyverse)
library(rlang)
```
</details>

User input in an ellipsis can be named or unnamed.
We can distinguish between those two kinds and make use of this distinction, in the following way creating a special interface for the function:

```{r include = FALSE}
# Combo: unnamed arguments define grouping, named arguments define summary
```
```{r 74-combo-unnamed-arguments-define-grouping-named-arguments-define-summary}
gsu <- function(.data, ...) {
  # Capture (quote) with enquos()
  quos <- enquos(...)

  is_named <- (names2(quos) != "")
  named_quos <- quos[is_named]
  unnamed_quos <- quos[!is_named]

  # Use (unquote-splice) with !!!
  .data %>%
    group_by(!!!unnamed_quos) %>%
    summarize(!!!named_quos) %>%
    ungroup()
}
```

The `named_quos` are our summary columns (name is name of the column, value is the expression to be used on the input column(s)) and the `unnamed_quos` are now the grouping columns:

```{r include = FALSE}
# Test it:
```
```{r 74-test-it}
mean_airtime_per_day <-
  nycflights13::flights %>%
  gsu(year, month, day, mean_air_time = mean(air_time, na.rm = TRUE))

mean_airtime_per_day
```
