```{r 76-remove-all, include = FALSE}
rm(list = ls())
```


## Argument names

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### Argument names

```
```{r 76-setup-76-names-r}
library(tidyverse)
library(rlang)
```
</details>

At the end of section [A custom plotting function](#colname) we defined a function `mutate_map_dbl()`.
A downside of this function was, that it did create the desired new column, but you weren't able to specify the column name in the function call.

Let's try to improve this aspect of the function:

```{r include = FALSE}
# A mutate_map() variant that allows naming the output column:
```
```{r 76-a-mutate-map-variant-that-allows-naming-the-output-column}
mutate_map_dbl <- function(.data, col, ...) {
  quos <- build_quos(!!enquo(col), ...)
  .data %>%
    mutate(!!!quos)
}

build_quos <- function(col, ...) {
  args <- list(...)
  stopifnot(length(args) == 1)

  expr <- args[[1]]

  map_quo <- build_map_quo(!!enquo(col), expr)

  set_names(list(map_quo), names(args))
}

build_map_quo <- function(col, expr) {
  quo <- enquo(col)
  quo(map_dbl(!!quo, expr))
}
```

Again, like in section [Names](#named) we are able to make use of the fact that an expression in an ellipsis of sorts `x = y` is treated in a way, that `x` is the name and `y` is the value of an object (here we used this in the code snippet `names(args)`).

A lot of things happen here:
1. the main function `mutate_map_dbl()` calls a helper function `build_quos()`
2. `build_quos()` in turn calls a helper's helper function `build_map_quo()`
3. `mutate_map_dbl()` then uses the output of the nested function calls to (hopefully) produce the desired result.

What output do the two helper functions produce? Let's test it:

```{r include = FALSE}
# Test it:
```
```{r 76-test-it}
build_quos(data, mean_petal_width = ~ mean(.$Petal.Width))

build_map_quo(mean_petal_width, ~ mean(.$Petal.Width))
```

And finally, let's see if our function lives up to our expectations:

```{r include = FALSE}
# Run it:
```
```{r 76-run-it}
iris %>%
  nest(-Species) %>%
  mutate_map_dbl(data, mean_petal_width = ~ mean(.$Petal.Width))
```

<!-- Now go and try to do this in base R :) -->
