```{r 77-remove-all, include = FALSE}
rm(list = ls())
```


## purrr-style mappers

<details><summary>*Click here to show setup code.*</summary>
```{r include = FALSE}
### purrr-style mappers

```
```{r 77-setup-77-mapper-r}
library(tidyverse)
library(rlang)

mutate_map_dbl <- function(.data, col, ...) {
  quos <- build_quos(!!enquo(col), ...)
  .data %>%
    mutate(!!!quos)
}
```
</details>

Is there still potential to improve our function `mutate_map_dbl()`?

We start here with only the highest level function definition of `mutate_map_dbl()` from section [Argument names](#argnames), i.e. without the definition of its helper functions `build_quos()` and `build_map_quo()`.

What we are trying to achieve now, is to rid ourselves from the need to provide the tilde before the function.
This is a slightly more tricky task, and here is how to go about it:

```{r include = FALSE}
# Refining build_quos() to get rid of the tilde:
```
```{r 77-refining-build-quos-to-get-rid-of-the-tilde}
build_quos <- function(col, ...) {
  args <- enquos(...)
  stopifnot(length(args) == 1)

  expr <- args[[1]]

  map_quo <- build_map_quo(!!enquo(col), !!expr)

  set_names(list(map_quo), names(args))
}

build_map_quo <- function(col, expr) {
  quo <- enquo(col)
  mapper <- as_mapper_quosure(!!enquo(expr))
  quo(map_dbl(!!quo, !!mapper))
}

as_mapper_quosure <- function(expr) {
  quo <- enquo(expr)

  rlang::new_function(
    alist(... = , . = ..1, .x = ..1, .y = ..2),
    quo_get_expr(quo),
    quo_get_env(quo)
  )
}
```

We needed to add one more level in the hierarchy of function calling.
The helper function `as_mapper_quosure()` creates a new function with the help of `rlang::new_function()`, which eventually makes it possible to leave out the tilde.

```{r include = FALSE}
# Test it:
```
```{r 77-test-it}
as_mapper(~ mean(.$Petal.Width))

as_mapper_quosure(mean(.$Petal.Width))

build_map_quo(mean_petal_width, mean(.$Petal.Width))
```

We see that our function `as_mapper_quosure()` is closely related to the function `purrr::as_mapper()`, but produces a quosure of a proper function and not a lambda function.
Also, it does not require the tilde.

So much to the theory, but does our main function also still behave in the right way?

```{r include = FALSE}
# Run it:
```
```{r 77-run-it}
iris %>%
  nest(-Species) %>%
  mutate_map_dbl(data, mean_petal_width = mean(.$Petal.Width))
```
